# Policy Representation and Public Responsiveness on Gender Equality [Still Very Drafty]

We want to know how public opinion responds to movement toward gender equality, but we think it makes sense to start the inquiry with the representation of opinion in politics and policy. 

## Representation: From Opinion to Politics and Policy

Typology of representation

Reasons for opinion to matter to policy

With regard to gender egalitarianism, the case for representation is straightforward: when the electorate holds a more gender-egalitarian view of women's roles in the public sphere, parties will run more women, more women will win election, and policies advancing gender equality will be more likely to pass.
Where traditional attitudes relegating women to the private sphere of home and children are more dominant, conversely, parties put forward fewer female candidates, fewer women gain office, and public policy will not change.
Indeed, @Beer2009 [, 214] says this story is so straightforward that it is tautological---that gender egalitarian public opinion itself "seems to be a very good measure of gender equality."

There are, however, many reasons for public opinion to not translate to policy.
sexist or even just skeptical party gatekeepers
institutional veto players
relative power of the wealthy

Here we should talk about why it _isn't_ tautological: belief vs behavior; institutions, including parties, that prevent preferences from being translated into outcomes* [for example, @Araujo2022, "As Powell Jr. (2004) describes, one of the obstacles to examining whether electorates' preferences translate into equivalent policy adoption is that 'a multidimensional preference configuration can yield almost any configuration of outcomes' (p. 291)" @Powell2004]; maybe additional reasons?

However, public opinion or preference is not always translated into policy outcomes. As @Monroe1998 mentioned in terms of policy consistency, policy changes or outcomes are not identical to a prior public preference. Policy consistency refers to the levels of match between public preferences for change and policy change.
In addition to the policy consistency, there are many reasons why public opinion or preference is not matched to policy outcomes. For instance, policy consistency can be determined by policy responsiveness. Previous studies have argued that policy responsiveness is a core democratic value for citizens and democratic countries rather than non-democratic countries tend to have higher policy responsiveness [@Bowler2017; @Miller2015]. Furthermore, a non-neglectable number of studies have demonstrated that there are variations concerning policy responsiveness in non-democratic countries according to their electoral systems or other socio-economic situations [@Dassonneville2021a; @Erikson2015; @Lueders2022; @Schakel2021]. Those studies are on the line with the argument that public opinion or preference is not always identical to policy outcomes. 
Also, there are many ways to explain the incongruency between policy and public opinion under democratic countries. For instance, it is plausible that political parties might focus on public opinion on salient issues rather than treat public preferences across all issues [@Alvarez2024; @Costello2021]. At the same time, the government and parliament them selves pay more attention to the global issues which received more public attention [@Kluver2016].


## Public Responsiveness: From Policy to Opinion

Thermostat: @Wlezien1995; @Soroka2010; @Atkinson2021

The research question is one right at the heart of the politics of inequality: When do women win office? And what part do public attitudes toward gender roles play in the process?
Not surprisingly, given the importance of the question, we have a range of theories on this.


```{r setup, include=FALSE}
options(tinytex.verbose = TRUE)

knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  dpi = 300,
  fig.width=7
)

if (!require(pacman))
  install.packages("pacman")
library(pacman)

p_install(janitor, force = FALSE)

p_load(
  # presentation
  RColorBrewer,
  colorRamps,
  directlabels,
  patchwork,
  naturalearth,
  
  # data wrangling
  broom,
  countrycode,
  DCPOtools,
  glue,
  here,
  janitor,
  tidyverse)

set.seed(324)

oecd_countries <- c("Australia", "Austria", "Belgium",
                    "Canada", "Chile", "Colombia",
                    "Costa Rica", "Czechia", "Denmark",
                    "Estonia", "Finland", "France", 
                    "Germany", "Greece", "Hungary",
                    "Iceland", "Ireland", "Israel",
                    "Italy", "Japan", "South Korea",
                    "Latvia", "Lithuania", "Luxembourg",
                    "Mexico", "Netherlands", "New Zealand",
                    "Norway", "Poland", "Portugal", 
                    "Slovakia", "Slovenia", "Spain",
                    "Sweden", "Switzerland", "Turkey", 
                    "United Kingdom", "United States")
```









### Dimensions of Political Equality
@Beer2009 [, 217]: "there is some scholarly consensus that gender equality should be assessed in terms of three domains: capabilities, opportunities, and empowerment/agency"

@Bericat2012: "education, work and power"


## The Scope of the Theory
But first we need to define the universe for the study.
As always, there are competing concerns.  
On the one hand, we want to look as broadly as possible: we want to minimize sampling bias that could influence our results and conclusions.
The desire to get beyond "just the U.S." or "just western Europe" was of course a big reason to generate the PGE data in the first place, to enable "cross-national, cross-regional" work.
But, on the other hand, we always need to avoid including cases to which the theory just doesn't apply.
The theories outlined above, at least those beyond the elite-led theory, the ones that have to do with public opinion, presuppose a certain minimum level of democracy--at least the minimal Przeworkski, Alvarez, Cheibub, and Limongi definition of democracy, "contested elections with broad suffrage for the most important offices"--and so countries that don't clear that very low bar should be excluded.
And politics works in many developing democracies in ways that suggest that the processes these theories describe may unfold very differently there--widespread clientelism, for example, is thought to work to exclude women from politics at every level [see, e.g, @Arriola2014; @Franceschet2014; @Benstead2015; @Paxton2021, 156-157].
So in light of these considerations, we are looking at advanced democracies.
It's important, though, to be sure to not interpret "advanced democracies" as simply "western Europe and the British offshoots."
And, further, one doesn't want to open the door to the garden of forking paths that comes with hand-picking the countries.
So we settled on the 38 countries of the current OECD.
Yes, it's the usual suspects of most of Europe plus the United States and 
Canada-Australia-New Zealand, but also Japan and Korea in east Asia, Turkey and Israel in west Asia, and Mexico, Costa Rica, Colombia, and Chile in Latin America.
Or, you know, about one China's worth of people; it's easy to see that there's still a lot of white countries to better understand also.
But the theories outlined in this chapter apply to these darker shaded countries, so they will be the subject of this book.

```{r oecdmap, fig.cap="The Cases Examined in This Book: The OECD \\label{oecdmap}", fig.height = 5.5, fig.width = 7.5}
world1 <- rnaturalearth::ne_countries(scale = "small", returnclass = "sf") %>%
    filter(!admin == "Antarctica")

world_geom <- world1 %>% 
  mutate(country = countrycode::countrycode(admin,
                                            "country.name",
                                            "country.name"),
         oecd = country %in% oecd_countries) %>% 
  filter(!admin == "Antarctica")

ggplot() +
  geom_sf(data = world1) +
  geom_sf(data = world_geom,
          aes(fill = oecd)) +
  coord_sf(crs = sf::st_crs("ESRI:53035")) +
  scale_fill_manual(name = "OECD Members", 
                    values = c("white", "grey50")) +
  theme(legend.position="none")
```
