# Policy Representation and Public Responsiveness on Gender Equality [Still Very Drafty]

```{r setup, include=FALSE}
options(tinytex.verbose = TRUE)

knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  dpi = 300,
  fig.width=7
)

if (!require(pacman))
  install.packages("pacman")
library(pacman)

p_install(janitor, force = FALSE)

p_load(
  # presentation
  RColorBrewer,
  colorRamps,
  directlabels,
  patchwork,
  naturalearth,
  
  # data wrangling
  broom,
  countrycode,
  DCPOtools,
  glue,
  here,
  janitor,
  tidyverse)

set.seed(324)

oecd_countries <- c("Australia", "Austria", "Belgium",
                    "Canada", "Chile", "Colombia",
                    "Costa Rica", "Czechia", "Denmark",
                    "Estonia", "Finland", "France", 
                    "Germany", "Greece", "Hungary",
                    "Iceland", "Ireland", "Israel",
                    "Italy", "Japan", "South Korea",
                    "Latvia", "Lithuania", "Luxembourg",
                    "Mexico", "Netherlands", "New Zealand",
                    "Norway", "Poland", "Portugal", 
                    "Slovakia", "Slovenia", "Spain",
                    "Sweden", "Switzerland", "Turkey", 
                    "United Kingdom", "United States")
```


We want to know how public opinion responds to movement toward gender equality, but we think it makes the most sense to start the inquiry with the representation of opinion in politics and policy. 

## Representation: From Opinion to Politics and Policy

Typology of representation: descriptive, substantive, symbolic [@Pitkin1967]

In public opinion research, policy representation occurs when policy change reflects changes in public opinion.

We consider _dynamic_ descriptive representation as whether changes in the share of women in the national legislature reflects gender egalitarian public opinion.
We use dynamic _substantive_ representation to refer to the question of whether changes in macroegalitarianism are reflected in changes in policies advancing gender equality.

Reasons for opinion, in general, to matter to politics and policy [@Miller2015; @Bowler2017; @Dassonneville2021a]

With regard to gender egalitarianism, the case for representation is straightforward: at least in democratic countries, when the electorate holds a more gender-egalitarian view of women's roles in the public sphere, parties will run more women, more women will win election, and policies advancing gender equality will be more likely to pass.
Where traditional attitudes relegating women to the private sphere of home and children are more dominant, conversely, parties put forward fewer female candidates, fewer women gain office, and anti-egalitarian public policy will not change.
Indeed, @Beer2009 [, 214] says this story is so straightforward that it is tautological---that gender egalitarian public opinion itself "seems to be a very good measure of gender equality."

There are, however, many reasons for gender egalitarian public opinion to _not_ translate to either more women in office or the adoption of policies that advance gender equality.

sexist or even just skeptical/anxious party gatekeepers

related: misperceptions of public opinion among legislators [@Walgrave2022]

competing issue priorities, both of voters and parties [see @Powell2004, 291; @Costello2021; @Alvarez2024; specifically with regard to gender attitudes, see @Hayes2016; @Araujo2022; and see also the emphasis on _autonomous_ women's movements in @Htun2012; @Forester2022] as well as straight-up failures in 'voting correctly' [see @Lau1997]

These competing issues may be brought forward through the greater relative power of the wealthy in an exercise of the second face of power [see, e.g., @Solt2008; @Erikson2015; @Schakel2021].

institutional veto players

(@Burstein2010 previews the opinion-to-policy debate.)

The argument for representation may appear strong, but to see if and to what extent the composition of legislatures and the content of policy represent the macroegalitarianism of the public, we are going to have to look.

How policy representation occurs: Is electoral turnover necessary or do legislators of all stripes respond to the public? (The latter is the 'policy accommodation' mechanism, per @Erikson2002.)  In this context, is it necessary for women to replace men in office for gender egalitarian policies to be adopted, or do men legislators also respond to macroegalitarianism in the public?


## Public Responsiveness: From Politics and Policy to Opinion

@Busemeyer2021 reviews.

Thermostatic public opinion: opinion moves opposite to policy [@Wlezien1995; @Soroka2010; @Atkinson2021]

Policies make their own constituencies: opinion moves to further support policy [@Svallfors2010; @Soss2007]

The public sometimes doesn't respond at all [@Atkinson2021]



### Policies Advancing Gender Equality

We focus on gender equality in the traditionally masculine public sphere of politics and paid employment.

@Beer2009 [, 217]: "there is some scholarly consensus that gender equality should be assessed in terms of three domains: capabilities, opportunities, and empowerment/agency"
@Bericat2012: "education, work and power"

The policies we consider, then, are among those @Htun2010 [, 210, 209] call _non-doctrinal_: they do not "touch upon the jurisdictional conflict between the state and other organizations over the administration of kinship relations, reproduction, and sexuality" and so do not "challenge religious doctrine or the codified tradition of a major cultural group."
This means, mercifully, that we don't have to also control for the strength of the church as an opponent to reform.


## The Scope of the Theory
Before we proceed further, we need to define the universe for the study.
As always, there are competing concerns.  
On the one hand, we want to look as broadly as possible: we want to minimize sampling bias that could influence our results and conclusions.
Too much work in political science 
The desire to get beyond "just the U.S." or "just western Europe" was of course a big reason to generate the PGE data in the first place, to enable "cross-national, cross-regional" work [see @Wilson2022].
But, on the other hand, we always need to avoid including cases to which the theory simply does not apply.
The theories outlined above presuppose a certain minimum level of democracy---at least the minimal Przeworkski, Alvarez, Cheibub, and Limongi definition of democracy, "contested elections with broad suffrage for the most important offices"---and so countries that don't clear that very low bar should be excluded.^[
This is not to say that governments in authoritarian countries do not at least sometimes work to represent public opinion.
In fact, there is reason to think---and evidence to show---that they sometimes do [see, e.g., @Tang2016 on China; @Lueders2022 on the German Democratic Republic].
Our point here is that the mechanisms through which public opinion may be translated to policy in authoritarian regimes is different from those suggested in the theories outlined above, and so for present purposes we should set those cases aside.]
And politics works in many developing democracies in ways that suggest that the processes these theories describe may unfold very differently there---widespread clientelism, for example, is thought to work to exclude women from politics at every level [see, e.g, @Arriola2014; @Franceschet2014; @Benstead2015; @Paxton2021, 156-157].
So in light of these considerations, we are looking at advanced democracies.
It's important, though, to be sure to not interpret "advanced democracies" as simply "western Europe and the British offshoots."
And, further, one doesn't want to open the door to the garden of forking paths that comes with hand-picking countries.
So we settled on the 38 countries of the current OECD (see @fig-oecdmap).
Yes, it's the usual suspects of most of Europe plus the United States and 
Canada-Australia-New Zealand, but also Japan and Korea in east Asia, Turkey and Israel in west Asia, and Mexico, Costa Rica, Colombia, and Chile in Latin America.
Or, you know, about one China's worth of people; it's easy to see that there's still a lot of other, unshaded countries to better understand also.
But the theories outlined in this chapter apply to these darker shaded countries, so they will be the subject of this book.

```{r oecdmap, fig.cap="The Cases Examined in This Book: The OECD", fig.height = 5.5, fig.width = 7.5}
#| label: fig-oecdmap

world1 <- rnaturalearth::ne_countries(scale = "small", returnclass = "sf") %>%
    filter(!admin == "Antarctica")

world_geom <- world1 %>% 
  mutate(country = countrycode::countrycode(admin,
                                            "country.name",
                                            "country.name"),
         oecd = country %in% oecd_countries) %>% 
  filter(!admin == "Antarctica")

ggplot() +
  geom_sf(data = world1) +
  geom_sf(data = world_geom,
          aes(fill = oecd)) +
  coord_sf(crs = sf::st_crs("ESRI:53035")) +
  scale_fill_manual(name = "OECD Members", 
                    values = c("white", "grey50")) +
  theme(legend.position="none")
```
