# Dynamic Substantive Representation

```{r setup, include=FALSE}
options(tinytex.verbose = TRUE)

knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  dpi = 300,
  fig.width=7
)

if (!require(pacman))
  install.packages("pacman")
library(pacman)

p_install(janitor, force = FALSE)

p_load(
  # analysis
  brms,
  
  # presentation
  gridExtra,
  modelsummary,
  dotwhisker,
  ggthemes,
  latex2exp,
  RColorBrewer,
  colorRamps,
  directlabels,
  patchwork,
  
  # data wrangling
  broom,
  countrycode,
  DCPOtools,
  glue,
  here,
  imputeTS,
  janitor,
  readxl,
  rsdmx,
  tidyverse,
  wbstats)

interplot2 <- function (m, var1, var2, plot = TRUE, steps = NULL, ci = 0.95, 
                        adjCI = FALSE, hist = FALSE, var2_dt = NA, predPro = FALSE, 
                        var2_vals = NULL, point = FALSE, sims = 5000, xmin = NA, 
                        xmax = NA, ercolor = NA, esize = 0.5, ralpha = 0.5, rfill = "grey70", 
                        stats_cp = "none", txt_caption = NULL, facet_labs = NULL, 
                        ...) {
  m.class <- class(m)
  if (m.class == "list") {
    m.sims <- m %>% 
      map_df(~ arm::sim(.x, sims/100) %>% 
               pluck("fixef") %>% 
               as_tibble())
    m <- m[[1]]
  } else m.sims <- arm::sim(m, sims) %>% 
      pluck("fixef") %>% 
      as_tibble()
  factor_v1 <- factor_v2 <- FALSE
  if (is.factor(eval(parse(text = paste0("m@frame$", var1)))) & 
      is.factor(eval(parse(text = paste0("m@frame$", var2))))) 
    stop("The function does not support interactions between two factors.")
  if (is.factor(eval(parse(text = paste0("m@frame$", var1))))) {
    var1_bk <- var1
    var1 <- paste0(var1, levels(eval(parse(text = paste0("m@frame$", 
                                                         var1)))))
    factor_v1 <- TRUE
    ifelse(var1 == var2, var12 <- paste0("I(", var1, "^2)"), 
           var12 <- paste0(var2, ":", var1)[-1])
    for (i in seq(var12)) {
      if (!var12[i] %in% unlist(dimnames(m@pp$X)[2])) 
        var12[i] <- paste0(var1, ":", var2)[-1][i]
      if (!var12[i] %in% unlist(dimnames(m@pp$X)[2])) 
        stop(paste("Model does not include the interaction of", 
                   var1, "and", var2, "."))
    }
  } else if (is.factor(eval(parse(text = paste0("m@frame$", 
                                                var2))))) {
    var2_bk <- var2
    var2 <- paste0(var2, levels(eval(parse(text = paste0("m@frame$", 
                                                         var2)))))
    factor_v2 <- TRUE
    ifelse(var1 == var2, var12 <- paste0("I(", var1, "^2)"), 
           var12 <- paste0(var2, ":", var1)[-1])
    for (i in seq(var12)) {
      if (!var12[i] %in% unlist(dimnames(m@pp$X)[2])) 
        var12[i] <- paste0(var1, ":", var2)[-1][i]
      if (!var12[i] %in% unlist(dimnames(m@pp$X)[2])) 
        stop(paste("Model does not include the interaction of", 
                   var1, "and", var2, "."))
    }
  } else {
    ifelse(var1 == var2, var12 <- paste0("I(", var1, "^2)"), 
           var12 <- paste0(var2, ":", var1))
    for (i in seq(var12)) {
      if (!var12[i] %in% unlist(dimnames(m@pp$X)[2])) 
        var12[i] <- paste0(var1, ":", var2)[i]
      if (!var12[i] %in% unlist(dimnames(m@pp$X)[2])) 
        stop(paste("Model does not include the interaction of", 
                   var1, "and", var2, "."))
    }
  }
  if (factor_v2) {
    xmin <- 0
    xmax <- 1
    steps <- 2
  } else {
    if (is.na(xmin)) 
      xmin <- min(m@frame[var2], na.rm = T)
    if (is.na(xmax)) 
      xmax <- max(m@frame[var2], na.rm = T)
    if (is.null(steps)) {
      steps <- eval(parse(text = paste0("length(unique(na.omit(m@frame$", 
                                        var2, ")))")))
    }
    if (steps > 100) 
      steps <- 100
  }
  coef <- data.frame(fake = seq(xmin, xmax, length.out = steps), 
                     coef1 = NA, ub = NA, lb = NA)
  coef_df <- data.frame(fake = numeric(0), coef1 = numeric(0), 
                        ub = numeric(0), lb = numeric(0), model = character(0))
  if (factor_v1) {
    if (predPro == TRUE) 
      stop("The current version does not support estimating predicted probabilities for factor base terms.")
    for (j in 1:(length(levels(eval(parse(text = paste0("m@frame$", 
                                                        var1_bk))))) - 1)) {
      for (i in 1:steps) {
        coef$coef1[i] <- mean(first(m.sims[, match(var1[j + 
                                                          1], unlist(dimnames(m@pp$X)[2]))] + coef$fake[i] * 
                                      m.sims[, match(var12[j], unlist(dimnames(m@pp$X)[2]))]))
        coef$ub[i] <- quantile(first(m.sims[, match(var1[j + 
                                                           1], unlist(dimnames(m@pp$X)[2]))] + coef$fake[i] * 
                                       m.sims[, match(var12[j], unlist(dimnames(m@pp$X)[2]))]), 
                               (1 - ci)/2)
        coef$lb[i] <- quantile(first(m.sims[, match(var1[j + 
                                                           1], unlist(dimnames(m@pp$X)[2]))] + coef$fake[i] * 
                                       m.sims[, match(var12[j], unlist(dimnames(m@pp$X)[2]))]), 
                               1 - (1 - ci)/2)
      }
      if (plot == TRUE) {
        coef$value <- var1[j + 1]
        coef_df <- rbind(coef_df, coef)
        if (hist == TRUE) {
          if (is.na(var2_dt)) {
            var2_dt <- eval(parse(text = paste0("m@frame$", 
                                                var2)))
          }
          else {
            var2_dt <- var2_dt
          }
        }
      }
      else {
        names(coef) <- c(var2, "coef", "ub", "lb")
        return(coef)
      }
    }
    if (is.null(facet_labs)) 
      facet_labs <- unique(coef_df$value)
    coef_df$value <- factor(coef_df$value, labels = facet_labs)
    interplot:::interplot.plot(m = coef_df, hist = hist, steps = steps, 
                               var2_dt = var2_dt, point = point, ercolor = ercolor, 
                               esize = esize, ralpha = ralpha, rfill = rfill, stats_cp = "none", 
                               txt_caption = NULL, ...) + facet_grid(. ~ value)
  } else if (factor_v2) {
    if (predPro == TRUE) 
      stop("The current version does not support estimating predicted probabilities for factor base terms.")
    for (j in 1:(length(levels(eval(parse(text = paste0("m@frame$", 
                                                        var2_bk))))) - 1)) {
      for (i in 1:steps) {
        coef$coef1[i] <- mean(first(m.sims[, match(var1, 
                                                   unlist(dimnames(m@pp$X)[2]))] + coef$fake[i] * 
                                      m.sims[, match(var12[j], unlist(dimnames(m@pp$X)[2]))]))
        coef$ub[i] <- quantile(first(m.sims[, match(var1, 
                                                    unlist(dimnames(m@pp$X)[2]))] + coef$fake[i] * 
                                       m.sims[, match(var12[j], unlist(dimnames(m@pp$X)[2]))]), 
                               (1 - ci)/2)
        coef$lb[i] <- quantile(first(m.sims[, match(var1, 
                                                    unlist(dimnames(m@pp$X)[2]))] + coef$fake[i] * 
                                       m.sims[, match(var12[j], unlist(dimnames(m@pp$X)[2]))]), 
                               1 - (1 - ci)/2)
      }
      if (plot == TRUE) {
        coef$value <- var2[j + 1]
        coef_df <- rbind(coef_df, coef)
        if (hist == TRUE) {
          if (is.na(var2_dt)) {
            var2_dt <- eval(parse(text = paste0("m@frame$", 
                                                var2)))
          }
          else {
            var2_dt <- var2_dt
          }
        }
      }
      else {
        names(coef) <- c(var2, "coef", "ub", "lb")
        return(coef)
      }
    }
    if (is.null(facet_labs)) 
      facet_labs <- unique(coef_df$value)
    coef_df$value <- factor(coef_df$value, labels = facet_labs)
    interplot:::interplot.plot(m = coef_df, steps = steps, hist = hist, 
                               var2_dt = var2_dt, point = point, ercolor = ercolor, 
                               esize = esize, ralpha = ralpha, rfill = rfill, stats_cp = "none", 
                               txt_caption = NULL, ...) + facet_grid(. ~ value)
  } else {
    if (predPro == TRUE) {
      if (is.null(var2_vals)) 
        stop("The predicted probabilities cannot be estimated without defining 'var2_vals'.")
      df <- data.frame(m$model)
      df[[names(m@flist)]] <- NULL
      if (sum(grep("X.weights.", names(df))) != 0) 
        df <- select(df, -X.weights.)
      df_temp <- select(df, 1)
      df <- df[-1] %>% map(function(var) {
        if (is.factor(var)) {
          model.matrix(~var - 1)[, -1] %>% as.data.frame()
        }
        else {
          as.numeric(var)
        }
      })
      for (i in seq(df)) {
        if (!is.data.frame(df[[i]])) {
          namesUpdate <- c(names(df_temp), names(df)[[i]])
          df_temp <- cbind(df_temp, df[[i]])
          names(df_temp) <- namesUpdate
        }
        else {
          df_temp <- cbind(df_temp, df[[i]])
        }
      }
      df <- df_temp
      names(df)[1] <- "(Intercept)"
      df$`(Intercept)` <- 1
      if (var1 == var2) {
        names(df) <- sub("I\\.(.*)\\.2\\.", "I\\(\\1\\^2\\)", 
                         names(df))
      }
      iv_medians <- summarize_all(df, funs(median(., na.rm = TRUE)))
      fake_data <- iv_medians[rep(1:nrow(iv_medians), 
                                  each = steps * length(var2_vals)), ]
      fake_data[[var1]] <- with(df, rep(seq(min(get(var1)), 
                                            max(get(var1)), length.out = steps), steps = length(var2_vals)))
      fake_data[[var2]] <- rep(var2_vals, each = steps)
      fake_data[[var12]] <- fake_data[[var1]] * fake_data[[var2]]
      pp <- rowMeans(plogis(data.matrix(fake_data) %*% 
                              t(data.matrix(m.sims))))
      row_quantiles <- function(x, probs) {
        naValue <- NA
        storage.mode(naValue) <- storage.mode(x)
        nrow <- nrow(x)
        q <- matrix(naValue, nrow = nrow, ncol = length(probs))
        if (nrow > 0L) {
          t <- quantile(x[1L, ], probs = probs)
          colnames(q) <- names(t)
          q[1L, ] <- t
          if (nrow >= 2L) {
            for (rr in 2:nrow) {
              q[rr, ] <- quantile(x[rr, ], probs = probs)
            }
          }
        }
        else {
          t <- quantile(0, probs = probs)
          colnames(q) <- names(t)
        }
        q <- drop(q)
        q
      }
      pp_bounds <- row_quantiles(plogis(data.matrix(fake_data) %*% 
                                          t(data.matrix(m.sims))), prob = c((1 - 
                                                                               ci)/2, 1 - (1 - ci)/2))
      pp <- cbind(pp, pp_bounds)
      pp <- pp * 100
      colnames(pp) <- c("coef1", "lb", "ub")
      pp <- cbind(fake_data[, c(var1, var2)], pp)
      pp[, var2] <- as.factor(pp[, var2])
      names(pp)[1] <- "fake"
      names(pp)[2] <- "value"
      coef <- pp
    } else {
      multiplier <- ifelse(var1 == var2, 2, 1) 
      
      for (i in 1:steps) {
        coef$coef1[i] <- mean(first(m.sims[, match(var1, 
                                                   unlist(dimnames(m@pp$X)[2]))] + {multiplier * 
                                                       coef$fake[i] * m.sims[, match(var12, 
                                                                                     unlist(dimnames(m@pp$X)[2]))]}))
        coef$ub[i] <- quantile(first(m.sims[, match(var1, 
                                                    unlist(dimnames(m@pp$X)[2]))] + multiplier * 
                                       coef$fake[i] * m.sims[, match(var12, 
                                                                     unlist(dimnames(m@pp$X)[2]))]), (1 - ci)/2)
        coef$lb[i] <- quantile(first(m.sims[, match(var1, 
                                                    unlist(dimnames(m@pp$X)[2]))] + multiplier * 
                                       coef$fake[i] * m.sims[, match(var12, 
                                                                     unlist(dimnames(m@pp$X)[2]))]), 1 - (1 - ci)/2)
      }
    }
    multiplier <- ifelse(var1 == var2, 2, 1) 
    min_sim <- m.sims[, match(var1, unlist(dimnames(m@pp$X)[2]))] + 
      multiplier * xmin * m.sims[, match(var12, 
                                         unlist(dimnames(m@pp$X)[2]))]
    max_sim <- m.sims[, match(var1, unlist(dimnames(m@pp$X)[2]))] + 
      multiplier * xmax * m.sims[, match(var12, 
                                         unlist(dimnames(m@pp$X)[2]))]
    diff <- first(max_sim - min_sim)
    ci_diff <- c(quantile(diff, (1 - ci)/2), quantile(diff, 
                                                      1 - (1 - ci)/2))
    if (plot == TRUE) {
      if (hist == TRUE) {
        if (is.na(var2_dt)) {
          var2_dt <- eval(parse(text = paste0("m@frame$", 
                                              var2)))
        }
        else {
          var2_dt <- var2_dt
        }
      }
      interplot:::interplot.plot(m = coef, steps = steps, hist = hist, 
                                 predPro = predPro, var2_vals = var2_vals, var2_dt = var2_dt, 
                                 point = point, ercolor = ercolor, esize = esize, 
                                 ralpha = ralpha, rfill = rfill, stats_cp = "none", 
                                 txt_caption = NULL, ...)
    } else {
      if (predPro == TRUE) {
        names(coef) <- c(var2, paste0("values_in_", 
                                      var1), "coef", "ub", "lb")
      }
      else {
        names(coef) <- c(var2, "coef", "ub", "lb")
      }
      return(coef)
    }
  }
}

interplot_b <- function (m, var1, var2, plot = TRUE, steps = NULL, ci = 0.95, 
                         adjCI = FALSE, hist = FALSE, var2_dt = NA, predPro = FALSE, 
                         var2_vals = NULL, point = FALSE, sims = 5000, xmin = NA, 
                         xmax = NA, ercolor = NA, esize = 0.5, ralpha = 0.5, rfill = "grey70", 
                         stats_cp = "none", txt_caption = NULL, facet_labs = NULL, 
                         ...) {
  
  m.sims <- brms::as_draws_df(m) %>% 
    as_tibble()
  
  if (is.na(xmin)) 
    xmin <- min(m$data[var2], na.rm = TRUE)
  if (is.na(xmax)) 
    xmax <- max(m$data[var2], na.rm = TRUE)
  if (is.null(steps)) {
    steps <- eval(parse(text = paste0("length(unique(na.omit(m$data$", 
                                      var2, ")))")))
  }
  if (steps > 100) 
    steps <- 100
  
  coef <- data.frame(fake = seq(xmin, xmax, length.out = steps), 
                     coef1 = NA, ub = NA, lb = NA)
  coef_df <- data.frame(fake = numeric(0), coef1 = numeric(0), 
                        ub = numeric(0), lb = numeric(0), model = character(0))
  
  var1a <- str_subset(names(m.sims), var1)[1]
  var2a <- str_subset(names(m.sims), var2)[1]
  ifelse(var1 == var2, var12 <- paste0("I(", var1, "^2)"), 
         var12 <- paste0(var2a, ":", var1))
  if (!var12 %in% names(m.sims))
    var12 <- paste0(var1a, ":", var2)
  if (!var12 %in% names(m.sims)) 
    stop(paste("Model does not include the interaction of", 
               var1, "and", var2, "."))
  
  multiplier <- ifelse(var1 == var2, 2, 1) 
  
  for (i in 1:steps) {
    coef$coef1[i] <- mean({m.sims[, var1a] + {multiplier * 
        coef$fake[i] * m.sims[, var12]}}[, 1])
    coef$lb[i] <- quantile({m.sims[, var1a] + {multiplier * 
        coef$fake[i] * m.sims[, var12]}}[, 1], (1 - ci)/2)
    coef$ub[i] <- quantile({m.sims[, var1a] + {multiplier * 
        coef$fake[i] * m.sims[, var12]}}[, 1], 1 - (1 - ci)/2)
  }
  
  min_sim <- {m.sims[, var1a] + {multiplier * 
      xmin * m.sims[, var12]}}[, 1]
  max_sim <- {m.sims[, var1a] + {multiplier * 
      xmax * m.sims[, var12]}}[, 1]
  diff <- first(max_sim - min_sim)
  ci_diff <- c(quantile(diff, (1 - ci)/2), quantile(diff, 
                                                    1 - (1 - ci)/2))
  if (plot == TRUE) {
    interplot:::interplot.plot(m = coef, steps = steps, hist = hist, 
                               predPro = predPro, var2_vals = var2_vals, var2_dt = var2_dt, 
                               point = point, ercolor = ercolor, esize = esize, 
                               ralpha = ralpha, rfill = rfill, stats_cp = "none", 
                               txt_caption = NULL, ...)
  } else {
    names(coef) <- c(var2, "coef", "ub", "lb")
    return(coef)
  }
}

make_dummies <- function(df, col) {
  vals <- discard(unique(df[[col]]), is.na)
  dummies <- map(vals, function(val) {
    df %>% 
      transmute({{val}} := as.numeric(.data[[col]] == val))
  }) %>% 
    list_cbind()
  
  bind_cols(df, dummies)
}

get_coef <- function(iv, results_df = coef_data, type = "both", width = .8) {
  result_var <- results_df %>% 
    filter(.width == width) %>% 
    pull(.variable) %>% 
    str_subset(iv)
  
  if (!type=="both") {
    res <- results_df %>% 
      filter(.variable == result_var & .width == width) %>% 
      pull({{type}})
  } else {
    sc <- results_df %>% 
      filter(.variable == result_var & .width == width) %>% 
      pull(std_coef)
    
    ci <- results_df %>% 
      filter(.variable == result_var & .width == width) %>% 
      pull(ci)
    
    wdth <- enexpr(width) * 100
    
    res <- paste0(sc, " (", wdth, "% c.i.: ", ci, ")")
  }
  
  return(res)
}

by2sd <- function(var) {
  dich <- stats::na.omit(unique(var)) %>% 
    sort() %>% identical(c(0, 1))
  if (dich) 
    sd <- 1
  else 
    sd <- 2 * stats::sd(var, na.rm = TRUE)
  
  return(sd)
}

set.seed(324)
descrep_path <- here("paper", "descriptive_representation")
policy_path <- here("paper", "policy_adoption")

oecd_countries <- c("Australia", "Austria", "Belgium",
                    "Canada", "Chile", "Colombia",
                    "Costa Rica", "Czechia", "Denmark",
                    "Estonia", "Finland", "France", 
                    "Germany", "Greece", "Hungary",
                    "Iceland", "Ireland", "Israel",
                    "Italy", "Japan", "South Korea",
                    "Latvia", "Lithuania", "Luxembourg",
                    "Mexico", "Netherlands", "New Zealand",
                    "Norway", "Poland", "Portugal", 
                    "Slovakia", "Slovenia", "Spain",
                    "Sweden", "Switzerland", "Turkey", 
                    "United Kingdom", "United States")
```

Definitions of substantive representation and dynamic representation, how do we get to dynamic substantive representation.
<!-- @Weeks2022a [,16]: measuring substantive representation is inherently difficult because intersectionality means women aren't monolithic -->

In this chapter, we consider policies that advance gender equality, first in  politics and then in the workplace.

We find

## Policies Advancing Gender Equality in Politics

One of the most-studied policies advancing gender equality is the adoption of gender quotas for candidates running for legislative seats.
National gender quotas---that is, candidate quotas instituted by law---mandate that women constitute a specified minimum share of each political party's candidates for the national legislature.
As we saw in the previous chapter, legislated national quotas have proven to be effective policies for increasing the share of women in office.

To measure the adoption and reform of quotas we again employ the data on the de facto threshold provided by the excellent QAROT database [@Hughes2019] updated with information from @IDEA2023.^[
There are other important aspects of national legislative quotas, such as whether and how they are enforced or if the position of women on an electoral list is specified [see, e.g., @Piscopo2024], but we leave these characteristics aside in this analysis.]

```{r dft_data3}

control_files <- c("qarot.rda", "des.rda", "fmi.rda", "gdppc.rda")
  
walk(control_files, \(f) 
     load(file.path(descrep_path, "data-raw", f), .GlobalEnv))

pge_summary <- rio::import(here("data",
                                "pge_summary.rda")) %>% 
  mutate(across(starts_with("p"),
                ~ .x * 100,
                .names = "{.col}"))
  
eee <- read_csv(file.path(descrep_path, "data-raw", "eee.csv"))

dft_data2 <- qarot %>% 
  filter(country %in% oecd_countries) %>% 
  full_join(pge_summary, by = join_by(country, year)) %>%
  left_join(des,
            by = c("countryname", "year")) %>%
  bind_rows(eee) %>% 
  left_join(fmi,
            by = c("country", "year")) %>% 
  group_by(country) %>% 
  mutate(countryname = country,
         iso2c = countrycode::countrycode(country, 
                                          "country.name",
                                          "iso2c",
                                          warn = FALSE),
         nq = defacto_threshold,
         pge_lag = lag(pge),
         pge_se_lag = lag(pge_se),
         fmi = if_else(country == "United States" & year < 1975, 3, fmi)) %>% 
  left_join(gdppc, by = c("country", "year")) %>% 
  mutate(gdppc = gdppc/10000) %>% 
  fill(list, .direction = "downup") %>% 
  fill(nq, women_rep) %>%
  mutate(nq_included = ifelse(!is.na(lag(pge)),
                              nq,
                              NA_real_)) %>% 
  ungroup() %>% 
  arrange(country, year) %>% 
  filter(country %in% oecd_countries) %>% 
  group_by(country) %>% 
  transmute(., 
            year,
            nq,
            nq_lag = if_else(row_number() == 1,
                             nq,
                             lag(nq)), # previous year
            nq_mean = mean(nq_lag, na.rm = TRUE),
            nq_diff = nq_lag - nq_mean,
            lnq = last(nq) + .0001*nq_mean,
            nq_included = ifelse(!is.na(pge_lag),
                                     nq,
                                     NA_real_),
            women_rep,
            women_rep_lag = lag(women_rep), # previous year
            women_rep_mean = mean(women_rep, na.rm = TRUE),
            women_rep_diff = women_rep - women_rep_mean,
            pge,
            pge_se,
            pge_lag, # previous year
            pge_se_lag, # previous year
            pge_mean = mean(pge_lag, na.rm = TRUE),
            pge_mean_se = sqrt(sum(pge_se_lag^2, na.rm = TRUE))/
              length(pge),
            pge_diff = pge_lag - pge_mean,
            pge_diff_se = sqrt(pge_se_lag^2 + pge_mean_se^2)/2,
            fmi,
            fmi_mean = mean(fmi, na.rm = TRUE),
            fmi_diff = fmi - fmi_mean,
            list,
            list_mean = mean(list, na.rm = TRUE),
            list_diff = list - list_mean,
            gdppc,
            gdppc_mean = mean(gdppc, na.rm = TRUE),
            gdppc_diff = gdppc - gdppc_mean) %>% 
  ungroup()

dft_data3 <- dft_data2 %>% 
  filter(., complete.cases(.))
```

```{r nqts, fig.cap="National Legislative Gender Quotas in the OECD", fig.height = 9, fig.width = 7.5}
#| label: fig-nqts

dft_data2 %>%
  ggplot(aes(x = year, y = nq)) +
  theme_bw() +
  theme(legend.position = "none") +
  coord_cartesian(xlim = c(1990, 2022)) +
  labs(x = NULL, y = "National Quota, De Facto Threshold") +
  geom_line(linetype = "dotted") +
  geom_line(aes(y = nq_included)) +
  facet_wrap(~reorder(country, -lnq), ncol = 6) +
  theme(axis.text.x  = element_text(size = 7,
                                    angle = 90,
                                    vjust = .45,
                                    hjust = .95),
        strip.text.x = element_text(size = 8),
        strip.background = element_rect(fill = "white", colour = "white"),
        plot.title = element_text(size=8)) +
  plot_annotation(caption = str_wrap("Note: Solid lines trace trends over the years covered in this chapter's analyses; dotted lines extend to years that were not\nincluded.  Sources: Hughes et al. (2019); International Institute for Democracy and Electoral Assistance (2023).", 80))
```

Recall that our measure of national quotas, first presented in the previous chapter, is the de facto threshold, which combines "a country's stated quota threshold and the breadth of a quota's actual reach" [@Hughes2019, 225].
@fig-nqts shows the trends in the adoption and reform of these national quotas over time.
Out of the thirty-eight countries of the OECD, four now have parity quotas, that is, half of the candidates run by each party must be women and half must be men: France, Belgium, Costa Rica, and Mexico.
Twelve additional countries have quotas with lower de facto thresholds, ranging from Italy's requirement that women comprise 46.25% quota of each party's candidates across all legislative seats to Greece's 33% mandate.
The remaining twenty-two OECD countries have no national legislative candidate quota at all.
In addition to these contrasts across countries, @fig-nqts shows that even the countries with parity quotas arrived at them via distinctively different routes.
France went from no quota at all to parity at once in 1999.
Belgium and Costa Rica adopted their 50% requirements in two steps, previously requiring 33% and 40% of parties' candidates to be women respectively, while Mexico took three, with earlier laws requiring 30% and then 40%.
Clearly quota adoption and reform has varied greatly across countries and over time.


### Substantive Representation in National Gender Quota Adoption

Does macroegalitarianism help us to explain these policy differences?
The bivariate relationship between the PGE scores and national legislative quotas in our data, depicted in @fig-nq-plot, is only weak.
Many countries, even those whose publics hold relatively egalitarian views on gender roles in the public sphere, have never adopted national gender quotas for legislative candidates; the dark, heavy line of observations across the bottom of the plot makes this clear.
However, to better assess whether these attitudes in the public make quota adoption more likely, we need to take into account other potential explanations.

```{r nqplot, fig.cap="Macroegalitarianism and National Quotas in the OECD", fig.height = 7, fig.width = 7.5}
#| label: fig-nq-plot
pge <- rio::import(here("data",
                        "pge.rda"))

nq_pge <- pge %>% 
  group_by(draw) %>% 
  group_split() %>% 
  map(. %>% 
        group_by(country) %>% 
        mutate(pge = pge*100) %>%
        ungroup() %>% 
        inner_join(dft_data3 %>% 
                     select(country, year, nq),
                   by = c("country", "year")))

nq_cor <- map(nq_pge,
              ~ with(.x,
                     cor(pge, nq,
                         use = "pairwise.complete.obs"))) %>% 
  unlist() %>% 
  mean() %>% 
  round(2) %>% 
  sprintf("%.2f", .) %>% 
  paste0("R = ", .)

nq_label <- tibble(pge_lag = 90,
                         nq = 4,
                         label = nq_cor)

nq_plot <- ggplot(dft_data3,
                  aes(x = pge_lag,
                      y = nq)) +
  geom_segment(aes(x = pge_lag-2*pge_se_lag, xend = pge_lag+2*pge_se_lag,
                   y = nq, yend = nq),
               na.rm = TRUE,
               alpha = .2) +
  geom_point(alpha = .2) +
  geom_smooth(method = 'lm', se = FALSE) +
  theme_bw() +
  theme(legend.position="none",
        axis.text  = element_text(size=10),
        axis.title = element_text(size=12)) +
  scale_x_continuous(limits=c(25, 100),
                     breaks=seq(25, 100, by = 25)) +
  scale_y_continuous(limits=c(0, 51)) +
  labs(x = TeX("Macroegalitarianism$_{t-1}$"), y = "National Quota") +
  geom_label(data = nq_label, aes(label = label))

nq_plot
```

A first factor often considered likely to influence the adoption of national legislative quotas is the extent of descriptive representation women have already achieved.
There are conflicting arguments, however, regarding _how_ descriptive representation shapes quota adoption.
From one perspective, as more women are elected to the legislature, they will be more likely to successfully push for quotas to be adopted and reformed [see, e.g., @Krook2009, 21-22; @Piscopo2024].
An opposing view holds that more descriptive representation for women works instead to undermine the sense of urgency that underpins the adoption of gender quotas [see, e.g., @Dahlerup2005; @Hughes2015]. 
To measure descriptive representation here, we use the same data from QAROT and the @IPU2023 on the percentage of legislative seats held by women that we employed in the previous chapter (see @fig-wrts).

Two other potential influences on legislative quota adoption and reform are also familiar from our previous chapter: feminist movement strength and electoral lists.
Feminist movements are frequently argued to be important to the success of the adoption and reform of national quotas [see @Paxton2021, 196].
As before, we rely on the Feminist Movement Index (FMI) [@Forester2022] as our measure of the strength of these movements (see Figure 4.5).
And consistent with arguments that electoral systems with at least a party-list component are more "woman-friendly" [@Rule1994, 27] and provide better opportunity structures for feminist activists, such electoral systems may make quota adoption and subsequent strengthening more likely as well [@Paxton2021, 195-196].
We again draw data on whether elections are held with a list component from the Democratic Electoral Systems Around the World dataset [@Bormann2022].

Our approach to modeling the adoption of gender quotas here is similar in several ways to the methods we employed in the previous chapter to model women's descriptive representation.
As in those analyses, we use a Bayesian multilevel model that includes varying intercepts for both space, which capture the idiosyncratic distinctiveness of each country, and time, which capture those shocks that operate on all countries in each year [see @Shor2007].
And also as in those analyses, we separate each of our time-varying predictors into its mean value for each country and the difference between its value in a given year and this country mean so as to avoid confusing the former, cross-country, differences with the over-time changes that provide the best evidence of causation [see @Bell2015].
Another commonality with the models used in the last chapter is that we again incorporate the measurement uncertainty in the PGE scores into our analysis to avoid drawing conclusions that are not supported by the data [see @Tai2024].

The fact that we are now seeking to explain policy adoption---and in particular the adoption of a gender quota---does, however, require a few differences in our modeling strategy.
The standard approach to modeling policy adoption is event history analysis (EHA) of pooled time series, popularized in political science by @Berry1990.
Event history analysis, in this context, typically involves a logistic regression of a dichotomous dependent variable observed annually in each country as a series of zeros followed by a one at the time the policy of interest is adopted.
Once a country adopts the policy, it is no longer part of the 'risk set'---that is, the country is not 'at risk' of adopting the policy a second time---and observations for that country in years subsequent to adoption are then dropped from the dataset [see @Berry1990, 398].

However, the general EHA approach is flexible [see @Boehmke2009].
The first reason this flexibility is important is that, as @Piscopo2024 explains and as the stair-step pattern often evident in @fig-nqts illustrates, many countries have not simply adopted quotas requiring a specified share of the candidates each party puts forward to be women but have also raised this share, sometimes repeatedly, to reach or at least more closely approach parity.
Removing a country from the analysis after its first quota adoption, as in the standard EHA approach described above, would prevent us from analyzing the 'steady path' [see @Piscopo2024] by which quotas are sometimes reformed.
We consider the adoption of a parity quota, one that requires 50% of a party's candidates across all seats to be women, to be the quota policy that maximally advances gender equality, and so a country leaves the risk set---and so further observations of the country are excluded from the data---only after it has adopted a parity quota.

A second reason this flexibility is important is because as seen above national legislative gender quotas and reforms are not all the same, either present or absent.
Recall that some countries---specifically France, Belgium, Costa Rica, and Mexico---now have quotas that require parity in the number of women and men each party puts forward as candidates across all legislative seats.
Other countries have adopted quotas that, although requiring parties to nominate _some_ women candidates, do not require parties to run equal numbers of women and men.
Still other countries, many in fact, have no mandatory legislative gender quota at all.
We therefore treat the adoption or reform of a quota as a continuous rather than dichotomous variable [see @Boehmke2009, 237].

In a final modification of the standard EHA approach, we take into account the dynamic nature of quota adoption and reform.
That is, we account for how the quota in force in the present depends on any mandated share of women candidates that was in force in the past by including the lagged value of the quota as a predictor.

```{r m1_nq}
if (!file.exists(file.path(policy_path,  "data", "m1_nq_results.rda"))) {
  bf_nq <- bf(nq ~
                me(pge_diff, pge_diff_se) +
                me(pge_mean, pge_mean_se) +
                women_rep_diff +
                women_rep_mean +
                fmi_diff +
                fmi_mean +
                list_diff +
                list_mean +
                nq_lag +
                (1|c|country) + (1|t|year))
  
  m1_nq_b <- brm(formula = bf_nq,
                 data = dft_data3 %>% 
                   filter(!nq_lag==50),
                 backend = "cmdstanr",
                 control=list(adapt_delta = 0.99, 
                              max_treedepth = 15),
                 warmup = 500,
                 iter = 1000,
                 chains = 4,
                 cores = 4,
                 seed = 324)
  
  m1_nq_data <- m1_nq_b$data
  
  m1_nq_data_2sd <- m1_nq_data %>% 
    select(-nq,
           -country, -year, -ends_with("_se")) %>% 
    summarize(across(everything(), by2sd)) %>% 
    pivot_longer(everything()) %>% 
    mutate(`.variable` = case_when(name == "pge_mean" ~ 
                                     "bsp_mepge_meanpge_mean_se",
                                   name == "pge_diff" ~
                                     "bsp_mepge_diffpge_diff_se",
                                   TRUE ~ paste0("b_", name)),
           var_names = c("Descriptive Representation, Difference",
                         "Descriptive Representation, Mean",
                         "Feminist Movement Strength, Difference",
                         "Feminist Movement Strength, Mean",
                         "Electoral List, Difference",
                         "Electoral List, Mean",
                         "Lagged Quota",
                         "Macroegalitarianism, Difference",
                         "Macroegalitarianism, Mean"),
           sd2 = ifelse(str_detect(.variable, "list_|fmi_diff|_lag"),
                        1,
                        value))
  
  coef_data0_m1_nq <- m1_nq_b %>% 
    tidybayes::gather_draws(`bs?p?_.*`, regex = TRUE) %>% 
    filter(!`.variable`=="b_Intercept") %>% 
    left_join(m1_nq_data_2sd, by = join_by(.variable))
  
  save(m1_national_quota_b, m1_nq_data_2sd, coef_data0_m1_nq, 
       file = file.path(policy_path, "data",  "m1_nq_results.rda"))
} else {
  load(file = file.path(policy_path, "data",  "m1_nq_results.rda"))
}
```

```{r m1nqplot, fig.cap="Predicting National Quotas in the OECD", fig.height = 7, fig.width = 7.5}
#| label: fig-m1-nq

ordered <- c("Macroegalitarianism, Difference",
             "Macroegalitarianism, Mean", 
             "Descriptive Representation, Difference",
             "Descriptive Representation, Mean",
             "Feminist Movement Strength, Difference",
             "Feminist Movement Strength, Mean", 
             "Electoral List, Difference",
             "Electoral List, Mean",
             "Lagged Quota") %>% 
  rev()

coef_data_m1_nq <- coef_data0_m1_nq %>% 
  mutate(std_coef = round(.value * sd2, 1),
         term = factor(var_names, levels = ordered)) %>%
  ggdist::median_qi(std_coef, .width = c(.8, .9)) %>%
  mutate(ci = paste0(round(.lower, 1), " to ", round(.upper, 1))) %>%
  left_join(m1_nq_data_2sd, ., by = join_by(.variable))

coef_data_m1_nq_total <- coef_data0_m1_nq %>% 
  group_by(.chain, .iteration, .draw) %>% 
  mutate(alpha = mean(ifelse(name=="nq_lag", .value, NA_real_),
                      na.rm = TRUE)) %>% 
  ungroup() %>% 
  group_by(.variable) %>% 
  mutate(std_coef0 = round(.value * sd2, 1),
         std_coef = round(std_coef0/(1 - alpha), 1),
         term = factor(var_names, levels = ordered)) %>%
  ggdist::median_qi(std_coef, .width = c(.8, .9)) %>%
  mutate(ci = paste0(round(.lower, 1), " to ", round(.upper, 1))) %>%
  left_join(m1_nq_data_2sd, ., by = join_by(.variable))

coef_plot_m1_nq <- coef_data0_m1_nq %>% 
  mutate(std_coef = .value * sd2,
         term = factor(var_names, levels = ordered)) %>% 
  filter(!str_detect(var_names, "Lagged")) %>% 
  ggplot(aes(y = term, x = std_coef)) +
  ggdist::stat_halfeye(.width = .8,
                       fill = "grey60",
                       linewidth = 2) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  theme_light() +
  # coord_cartesian(xlim = c(-15, 15)) +
  xlab("Standardized Coefficients") +
  ylab(NULL)

lag_plot_m1_nq <- coef_data0_m1_nq %>% 
  mutate(std_coef = .value * sd2,
         term = factor(var_names, levels = ordered)) %>% 
  filter(str_detect(var_names, "Lagged")) %>% 
  mutate(term = "Lagged National Quota") %>% 
  ggplot(aes(y = term, x = std_coef)) +
  ggdist::stat_halfeye(.width = .8,
                       fill = "grey60",
                       linewidth = 2) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  theme_light() +
  theme(strip.text.x = element_blank(),
        strip.background = element_blank()) +
  xlab("Unstandardized Coefficient") +
  ylab(NULL)

coef_plot_m1_nq + lag_plot_m1_nq +
  plot_layout(ncol = 1, widths = c(1, 1), heights = c(8, 1)) +
  plot_annotation(caption = "Notes: Dots indicate posterior medians; whiskers describe 80% credible\nintervals; shading depicts the posterior probability distribution.")
```

@fig-m1-nq presents the results.
Starting with the bottom panel, we see that quota laws are strongly dynamic: not surprisingly, even accounting for the other variables in the model, the extent to which the law requires parties to run women candidates for the national legislature this year is strongly influenced by the state of the law last year.
The adoption of new quota policies and the reform of old ones are relatively rare.

Moving upward, we next see the estimated coefficients for differences between electoral systems with a party list component as compared to systems that include only personalized races run by candidates within districts.
Countries in which all of the observed legislative terms were held with electoral systems with a list component enacted quota laws mandating that `r get_coef("list_mean", coef_data_m1_nq)` percentage points more candidates are women in one year than those that have never held elections with party lists, with a posterior probability that---conditional on these data and this model---that this estimate is positive of `r {{coef_data0_m1_nq %>% filter(name == "list_mean" & .value > 0) %>% nrow()}/20} %>% round()`%.
Given the strongly dynamic nature of quota laws, with differences this year persisting into the future, this seemingly small estimate stretches to `r get_coef("list_mean", coef_data_m1_nq)` points over time.
While this result provides some evidence that electoral systems have long-run effects, we cannot rule out unobserved confounding variables correlated with these mean scores.
And the coefficient for the _difference_ in electoral lists within a country provides no evidence that adopting a party-list electoral system yields a higher quota of women candidates in the short run.
A causal interpretation of the association between electoral lists and gender quota adoption remains unsupported.

We turn then to the strength of the autonomous feminist movement.
Countries that have experienced higher mean scores on the Feminist Movement Index are estimated to be little different from those with lower mean FMI scores.
In any event, the best evidence that stronger feminist movements lead to more demanding gender quotas comes from the estimated coefficient for 
changes in the strength of the feminist movement over time.
A one-point increase in the FMI index over time within a country is estimated to yield a subsequent increase in the country's legislative quota of `r get_coef("fmi_diff", coef_data_m1_nq)` percentage points immediately and `r get_coef("fmi_diff", coef_data_m1_nq_total)` over time.
This is powerful evidence that when feminist movements grow stronger they are more successful in their advocacy for higher quotas.

As to the debate regarding whether more women in office creates more or less pressure for legislative quotas, this evidence falls more on the latter side.
A countries with a mean level of women's descriptive representation a standard deviation above the overall mean is estimated to have a mandated share of women candidates that is on average `r get_coef("women_rep_mean", coef_data_m1_nq) %>% str_replace_all("-", "")` points _lower_ than a country with mean women's descriptive representation a standard deviation below the overall mean.
This decline grows with time to `r get_coef("women_rep_mean", coef_data_m1_nq_total) %>% str_replace_all("-", "")`.
Increases in women's descriptive representation within a country over time, on the other hand, appear to have little impact on quota adoption either way.

The top two rows of the panel display the evidence in support of the argument that gender egalitarian public opinion shapes the extent of success in enacting legislative candidate gender quotas.
This evidence is strong.
A country with mean PGE scores two standard deviations higher, for example New Zealand as compared to Poland, is estimated to enact quotas requiring `r get_coef("pge_mean", coef_data_m1_nq)` percentage points more women candidates, a difference that grows dynamically to `r get_coef("pge_mean", coef_data_m1_nq_total)` points.
As we have been careful to note previously, cross-country estimates like this one provides some evidence of an effect---in this case, of a more egalitarian public on legislative quota adoption---over the long term, but they could also reflect other differences among countries correlated with the predictor, here public opinion, that we are unable to measure and include in our model.
That is, such estimates could be the result of omitted-variable bias.
Therefore, although suggestive of causal effects, the real work of this estimate is to isolate the consequences of changes in public gender egalitarianism over time.

This estimate, the coefficient for within-country changes in PGE over time, is shown in the top row of the figure.
A two-standard-deviations increase in this variable---equivalent to about a twelve-point change in the PGE score from the start of one legislative term to the beginning of the next---is estimated to yield a `r get_coef("pge_diff", coef_data_m1_nq, type = "std_coef")` percentage-point increase in a country's legislative candidate quota in the following year, with an 80% confidence interval from `r get_coef("pge_diff", coef_data_m1_nq, type = "ci")` points.
Over time, this increase is estimated to grow to `r get_coef("pge_diff", coef_data_m1_nq_total)` points.
This is strong evidence that when the public of a country grows more egalitarian in its views of gender roles in politics and the workplace, lawmakers respond by enacting higher legislative candidate quotas.
Macroegalitarianism matters to electoral policy adoption.

As we saw in the previous chapter, when and where the public holds more gender egalitarian views, women are more successful in gaining elected office.
By including descriptive representation, the share of women legislators in office, in our model we effectively partition off that potential causal path.
In other words, the positive effect of public opinion on gender quota adoption just described does not work through the number of women elected to office.
Instead, these results support the argument that, at least among these rich OECD democracies, both men and women legislators are responsive to growing public demand for gender equality, and they respond with policies that increase the mandated share of women candidates for legislative office.


### Public Responsiveness to National Gender Quota Adoption

Does quota adoption trigger a backlash?
Or do quotas work to help make gender equality salient, as @Weeks2022 puts it, and so increase macroegalitarianism?
Or is the public simply unresponsive to policy change, leaving the relationship between opinion and policy flowing entirely from the former to the latter?
The extensive data on macroegalitarianism that we presented in Chapter 3, stretching across decades in all of the OECD countries, allows us to investigate these questions.

As in the previous chapter we model the potentially reciprocal relationships between our two variables of greatest interest using two equations, the first for quota adoption and reform and the second for macroegalitarianism, that are estimated together within a multivariate simultaneous equations model.
Past macroegalitarianism is used to predict present quotas, and past quotas are used to predict present macroegalitarianism.
The varying intercepts for each country and year in the two equations are treated as correlated, which works to tie them both together in a single model.

```{r nqsem_results}    
if (!file.exists(file.path(policy_path, "data", "nqsem_results.rda"))) {  
  bf_pge <- bf(pge ~ 
                 nq_diff +
                 nq_mean +
                 women_rep_diff +
                 women_rep_mean +
                 fmi_diff +
                 fmi_mean +
                 list_diff +
                 list_mean +
                 gdppc_diff +
                 gdppc_mean +
                 pge_lag +
                 (1|c|country) + (1|t|year))
  
  m2_nqsem_b <- brm(formula = bf_nq + 
                      bf_pge + 
                      set_rescor(TRUE),  
                    data = dft_data3 %>% 
                      filter(!nq_lag==50),
                    backend = "cmdstanr",
                    control=list(adapt_delta = 0.99, 
                                 max_treedepth = 16),
                    warmup = 500, 
                    iter = 1000, 
                    chains = 4, 
                    cores = 4,
                    seed = 324)
  
  m2_data <- m2_nqsem_b$data
  
  m2_data_2sd <- m2_data %>% 
    select(pge_diff,
           pge_mean,
           women_rep_diff,
           women_rep_mean,
           fmi_diff,
           fmi_mean,
           list_diff,
           list_mean,
           nq_lag) %>% 
    summarize(across(everything(), by2sd)) %>% 
    pivot_longer(everything()) %>% 
    mutate(`.variable` = case_when(name == "pge_mean" ~ 
                                     "bsp_nq_mepge_meanpge_mean_se",
                                   name == "pge_diff" ~
                                     "bsp_nq_mepge_diffpge_diff_se",
                                   TRUE ~ paste0("b_nq_", name)),
           var_names = c("Macroegalitarianism, Difference",
                         "Macroegalitarianism, Mean",
                         "Descriptive Representation, Difference",
                         "Descriptive Representation, Mean",
                         "Feminist Movement Index, Difference",
                         "Feminist Movement Index, Mean",
                         "Electoral List, Difference",
                         "Electoral List, Mean",
                         "Lagged National Quota"
           ),
           sd2 = ifelse(str_detect(.variable, "list_|_lag"),
                        1,
                        value),
           dv = "National Quota") %>% 
    bind_rows(m2_data %>% 
                select(nq_diff,
                       nq_mean,
                       women_rep_diff,
                       women_rep_mean,
                       fmi_diff,
                       fmi_mean,
                       list_diff,
                       list_mean,
                       gdppc_diff,
                       gdppc_mean,
                       pge_lag) %>% 
                summarize(across(everything(), by2sd)) %>% 
                pivot_longer(everything()) %>% 
                mutate(`.variable` = paste0("b_pge_", name),
                       var_names = c("National Quota, Difference",
                                     "National Quota, Mean",
                                     "Descriptive Representation, Difference",
                                     "Descriptive Representation, Mean",
                                     "Feminist Movement Index, Difference",
                                     "Feminist Movement Index, Mean",
                                     "Electoral List, Difference",
                                     "Electoral List, Mean",
                                     "GDP per Capita, Difference",
                                     "GDP per Capita, Mean",
                                     "Lagged Macroegalitarianism"
                       ),
                       sd2 = ifelse(str_detect(.variable, "list_|_lag"),
                                    1,
                                    value),
                       dv = "Macroegalitarianism")) %>% 
    mutate(dv = factor(dv, levels = c("National Quota",
                                      "Macroegalitarianism")))
  
  coef_data0_nqsem <- m2_nqsem_b %>% 
    as_draws_df() %>% 
    tidybayes::gather_draws(`bs?p?_.*`, regex = TRUE) %>% 
    filter(!str_detect(`.variable`, "_Intercept")) %>% 
    left_join(m2_data_2sd, by = join_by(.variable))
  
  save(m2_data, m2_data_2sd, coef_data0_nqsem, 
       file = file.path(policy_path,
                        "data",
                        "nqsem_results.rda"))
} else {
  load(file = file.path(policy_path, "data", "nqsem_results.rda"))
}
```

```{r m2nqplot, fig.cap="Predicting National Quota Adoption and Macroegalitarianism in OECD Countries", fig.height = 9, fig.width = 7.5}
#| label: fig-m2-nq

ordered_nqsem <- c("Macroegalitarianism, Difference",
                   "Macroegalitarianism, Mean", 
                   "National Quota, Difference",
                   "National Quota, Mean",
                   "Descriptive Representation, Difference",
                   "Descriptive Representation, Mean",
                   "Feminist Movement Index, Difference",
                   "Feminist Movement Index, Mean",
                   "Electoral List, Difference",
                   "Electoral List, Mean",
                   "GDP per Capita, Difference",
                   "GDP per Capita, Mean",
                   "Lagged National Quota",
                   "Lagged Macroegalitarianism") %>% 
  rev()

coef_data_nqsem <- coef_data0_nqsem %>% 
  mutate(std_coef = round(.value * sd2, 2),
         term = factor(var_names, levels = ordered_nqsem)) %>%
  ggdist::median_qi(std_coef, .width = c(.8, .9)) %>%
  mutate(ci = paste0(round(.lower, 1), " to ", round(.upper, 1))) %>%
  left_join(m2_data_2sd, ., by = join_by(.variable))

coef_data_nqsem_total <- coef_data0_nqsem %>%  
  group_by(.chain, .iteration, .draw) %>% 
  mutate(alpha_nq = mean(ifelse(name=="nq_lag", .value, NA_real_),
                         na.rm = TRUE),
         alpha_pge = mean(ifelse(name=="pge_lag", .value, NA_real_),
                          na.rm = TRUE)) %>% 
  ungroup() %>% 
  group_by(.variable) %>% 
  mutate(std_coef0 = round(.value * sd2, 1),
         std_coef = if_else(dv == "National Quota",
                            round(std_coef0/(1 - alpha_nq), 1),
                            round(std_coef0/(1 - alpha_pge), 1)),
         term = factor(var_names, levels = ordered_nqsem)) %>%
  ggdist::median_qi(std_coef, .width = c(.8, .9)) %>%
  mutate(ci = paste0(round(.lower, 1), " to ", round(.upper, 1))) %>%
  right_join(m2_data_2sd, by = join_by(.variable))

coef_plots_nqsem <- coef_data0_nqsem %>% 
  mutate(std_coef = .value * sd2,
         term = factor(var_names, levels = ordered_nqsem)) %>% 
  filter(!str_detect(var_names, "Lagged")) %>% 
  ggplot(aes(y = term, x = std_coef)) +
  ggdist::stat_halfeye(.width = .8,
                       fill = "grey60",
                       linewidth = 2) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  facet_grid(~ dv) +
  coord_cartesian(x = c(-2, 2)) +
  theme_light() +
  theme(strip.text.x = element_text(size = 10, color = "black"),
        strip.background = element_rect(fill = "white", colour = "white")) +
  xlab("Standardized Coefficients") +
  ylab(NULL)

lag_plots_nqsem <- coef_data0_nqsem %>% 
  mutate(std_coef = .value * sd2,
         term = factor(var_names, levels = ordered_nqsem)) %>% 
  filter(str_detect(var_names, "Lagged")) %>% 
  mutate(term = "Lagged Response Variable") %>% 
  ggplot(aes(y = term, x = std_coef)) +
  ggdist::stat_halfeye(.width = .8,
                       fill = "grey60",
                       linewidth = 2) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  facet_grid(~ dv) +
  theme_light() +
  theme(strip.text.x = element_blank(),
        strip.background = element_blank()) +
  xlab("Unstandardized Coefficients") +
  ylab(NULL) 

coef_plots_nqsem + lag_plots_nqsem +
  plot_layout(ncol = 1, widths = c(1, 1), heights = c(11, 1)) +
  plot_annotation(caption = "Notes: Dots indicate posterior medians; whiskers describe 80% credible\nintervals; shading depicts the posterior probability distribution.")
```

@fig-m2-nq presents the results of this simultaneous equations model.
Consider first the left panel of the figure, which shows the estimates of the equation predicting national quota adoption.
It provides additional support for the conclusions we drew from the findings presented in @fig-m1-nq: macroegalitarianism predicts national quota adoption and reform in both the short term, as evidenced by the estimate for its difference, and the long term, as evidenced by the estimate for its mean.
Countries with higher mean descriptive representation are less likely to adopt quotas, consistent with the 'incremental track' identified in @Dahlerup2005.
Increases in feminist movement strength appear to prompt higher quotas, and countries with more experience with list electoral systems are found to be more likely to adopt quotas as well.
In other words, the results presented on policy representation above in @fig-m1-nq are not markedly influenced by simultaneity bias.

This is reassuring, but it is really the right side of the figure that is now our focus.
That side shows the model's results for macroegalitarianism.
And so it is that side that speaks to the question of whether quotas 'create their own constituencies' or instead trigger among the public a thermostatic backlash against gender equality.
Before we reach that answer, however, we again start at the bottom of the plot with the estimates for our control variables.

After the estimate of the strongly dynamic effect of past values of macroegalitarianism on present values in the bottom right panel, the two bottom rows of the top right panel present the estimates for GDP per capita.
As in @fig-m3-wr in the previous chapter, these estimates show support for modernization theory [see, e.g., @Inglehart2000; @Inglehart2003].
Countries with higher GDP per capita exhibit more macroegalitarianism: compared to a country that is a standard deviation below the mean on this variable, a country that is a standard deviation above is predicted to have a PGE score `r get_coef("gdppc_mean", coef_data_nqsem)` points higher, compounding over time in this dynamic model to `r get_coef("gdppc_mean", coef_data_nqsem_total)` points.
This evidence from cross-country differences even within the OECD for a long-run effect of economic modernization is matched by the result for within-country differences.
A two-standard-deviation gain in GDP per capita from one year to the next is estimated to yield an increase of `r get_coef("gdppc_diff", coef_data_nqsem)` points in a country's PGE score.
This increase then grows to a total of `r get_coef("gdppc_diff", coef_data_nqsem_total)` over time.

Next are the estimates for electoral systems with a party-list component.
As was also seen in @fig-m3-wr in the last chapter, net of the other variables in the model, countries that elect at least some legislators via a party list are estimated to have less macroegalitarianism than those with only more candidate-oriented single-member or small multi-member districts.
In this model, this difference in PGE scores is estimated as `r coef_data_nqsem %>% filter(.variable == "b_pge_list_mean" & .width == .8) %>% glue_data("{std_coef} (80% c.i. {ci})") %>% str_remove_all("-")` points, growing over time to `r coef_data_nqsem_total %>% filter(.variable == "b_pge_list_mean" & .width == .8) %>% glue_data("{std_coef} (80% c.i. {ci})") %>% str_remove_all("-")` points.
Whether this is a true long-run effect of list electoral systems or instead the result of some other, unmeasured and omitted variable is unclear.
The latter interpretation is perhaps reinforced by the inconclusive posterior distribution for differences over time in such electoral systems, although that distribution is mostly negative and its width is at least partially the product of the near absence in our dataset of changes in this variable within countries. 
There is no evidence that the strength of the feminist movement has a direct effect on macroegalitarianism in these results.
Neither cross-country differences nor within-country year-to-year changes yield estimates that are little different from zero.

As we have seen previously, the same cannot be said for women's descriptive representation.
Countries that have elected more women over the timeframe examined here exhibit higher levels of macroegalitarianism on average than those that have elected fewer women, consistent with a long-term effect.
A two-standard-deviation difference in cross-country means is estimated to correspond to `r coef_data_nqsem %>% filter(.variable == "b_pge_women_rep_mean" & .width == .8) %>% glue_data("{std_coef} (80% c.i. {ci})")` points higher PGE scores.
Thanks to the strong influence of past values of macroegalitarianism on present and future values, this jump up is estimated to grow over time to `r coef_data_nqsem_total %>% filter(.variable == "b_pge_women_rep_mean" & .width == .8) %>% glue_data("{std_coef} (80% c.i. {ci})")` points.
Similarly, a two-standard-deviation increase in descriptive representation in one year is estimated to correspond to `r coef_data_nqsem %>% filter(.variable == "b_pge_women_rep_diff" & .width == .8) %>% glue_data("{std_coef} (80% c.i. {ci})")` point gain in macroegalitarianism in the next, which increases over time to `r coef_data_nqsem_total %>% filter(.variable == "b_pge_women_rep_diff" & .width == .8) %>% glue_data("{std_coef} (80% c.i. {ci})")` points.

Finally, we arrive at the estimates for national quotas.
The results are mixed.
On the one hand, countries that have had higher average quotas over the years examined exhibit more macroegalitarianism than countries that had lower average quotas.
A country with a mean quota of 9.6%, a value similar to those of Spain and South Korea, is estimated to have PGE scores `r get_coef("pge_mean", coef_data_nqsem)` points higher than an otherwise similar country that never adopted a national legislative gender quota; over time, this estimated difference grows to `r get_coef("pge_mean", coef_data_nqsem_total)` points.
So, with all of the caveats that should now be familiar regarding cross-national differences and potential omitted variables, this result points to a positive reinforcement of macroegalitarianism by national legislative quotas.
On the other hand, quota adoptions _within_ a country's timeline do not appear to influence later macroegalitarianism at all: the dashed vertical line a zero bisects the posterior distribution for this estimate very nearly perfectly.
The one conclusion that is safe to draw from these results is that the adoption and reform of national legislative gender quotas do _not_ provoke a negative response in the public.
There is no evidence whatsoever of anti-egalitarian backlash.


## Policies Advancing Gender Equality in the Workplace

**Intro paragraph needed here.**

To measure policies advancing gender equality in the workplace, we rely on the World Bank's Women, Business, and Law v1.0 (WBL) policy index [@WorldBank2024].
As shown in @tbl-wbl, the WBL policy index comprises thirty-five policies addressing eight topics meant "to capture inequality in legislation throughout the duration of a womans working life, from the time she can enter the labor force through to retirement" [@Hyland2020, 476].
Each is a provision enhancing gender equality in the law.
The WBL policy index's _de jure_ rather than _de facto_ nature makes the index especially suited for our purposes because it ensures we are considering not policy outcomes but policy outputs.
Outcomes, the extent to which a goal is achieved, are clearly important.
But representation is better measured not by what governments achieve---which may after all be influenced by many factors beyond their control---but the steps they take (or fail to take) to reach those goals.

We hasten to add that the WBL policies do appear to get results.
Cross-sectionally, in countries with more of these policies, @Htun2019 found that women have greater access to economic resources: more access to bank accounts, higher ownership of firms, more participation in the labor force, and smaller gender wage gaps.
Looking across countries and over time, their adoption has been shown to be closely linked to subsequently increased women's labor force participation rates, both in the OECD [@Gonzales2015, 21-23] and beyond [@Gonzales2015, 25-26; @Hyland2020, 478-488].
Increases in the WBL policy index also yield narrowing gaps in the wages earned by men and women [@Hyland2020, 478-488].
The WBL policies listed in @tbl-wbl are not only actionable but also effective.

```{r wbl}
if (!file.exists(file.path(policy_path,
                           "data-raw",
                           "wbl2024_v1.xlsx"))) {
  download.file("https://wbl.worldbank.org/content/dam/sites/wbl/documents/2024/WBL2024-1-0-Historical-Panel-Data.xlsx",
              file.path(policy_path,
                           "data-raw",
                           "wbl2024_v1.xlsx"))
}

if (!file.exists(file.path(policy_path, "data-raw", "wbl.rda"))) {
  control_files <- c("qarot.rda", "des.rda", "fmi.rda", "gdppc.rda")
  
  walk(control_files, \(f) 
       load(file.path(descrep_path, "data-raw", f), .GlobalEnv))
  
  wbl_data <- read_excel(file.path(policy_path,
                                   "data-raw",
                                   "wbl2024_v1.xlsx"),
                         sheet = "WBL Panel 2024") %>% 
    janitor::clean_names() %>% 
    mutate(country = countrycode(economy, "country.name", "country.name"),
           year = as.numeric(report_year),
           wbl = wbl_index) %>% 
    full_join(pge_summary, by = join_by(country, year)) %>%
    left_join(qarot,
              by = c("country" = "countryname", "year")) %>% 
    left_join(des,
              by = c("country" ="countryname", "year")) %>%
    left_join(fmi,
              by = c("country", "year")) %>% 
    group_by(country) %>% 
    mutate(countryname = country,
           iso2c = countrycode::countrycode(country, 
                                            "country.name",
                                            "iso2c",
                                            warn = FALSE),
           pge_lag = lag(pge),
           pge_se_lag = lag(pge_se),
           fmi = if_else(country == "United States" & year < 1975, 3, fmi),
           wbl_included = ifelse(!is.na(lag(pge)),
                                            wbl,
                                            NA_real_),
           wbl_lag = lag(wbl),
           national_quota = if_else(is.na(defacto_threshold), 0,
                                    defacto_threshold)) %>% 
    left_join(gdppc, by = c("country", "year")) %>% 
    mutate(gdppc = gdppc/10000) %>% 
    fill(list) %>% 
    ungroup() %>% 
    arrange(country, year) %>% 
    filter(country %in% oecd_countries)

  
  wbl_parent <- read_excel(file.path(policy_path,
                                     "data-raw",
                                     "wbl2024_v1.xlsx"),
                           sheet = "Parenthood") %>% 
    janitor::clean_names() %>% 
    mutate(country = countrycode(economy, "country.name", "country.name"),
           year = as.numeric(report_year),
           wbl_parent = parenthood_score/20) %>% 
    filter(country %in% oecd_countries) %>% 
    full_join(pge_summary, by = join_by(country, year)) %>%
    left_join(qarot,
              by = c("country" = "countryname", "year")) %>% 
    left_join(des,
              by = c("country" ="countryname", "year")) %>%
    left_join(fmi,
              by = c("country", "year")) %>% 
    group_by(country) %>% 
    mutate(countryname = country,
           iso2c = countrycode::countrycode(country, 
                                            "country.name",
                                            "iso2c",
                                            warn = FALSE),
           pge_lag = lag(pge),
           pge_se_lag = lag(pge_se),
           fmi = if_else(country == "United States" & year < 1975, 3, fmi),
           wbl_parent_included = ifelse(!is.na(lag(pge)),
                                            wbl,
                                            NA_real_),
           wbl_parent_reform = wbl_parent - lag(wbl_parent),
           national_quota = if_else(is.na(defacto_threshold), 0,
                                    defacto_threshold)) %>% 
    left_join(gdppc, by = c("country", "year")) %>% 
    mutate(gdppc = gdppc/10000) %>% 
    fill(list) %>% 
    ungroup() %>% 
    arrange(country, year)
  
  save(wbl_data, wbl_parent, file = file.path(policy_path,
                                              "data-raw",
                                              "wbl.rda"))
} else {
  load(file.path(policy_path, "data-raw", "wbl.rda"))
}
```

```{r tblwbl}
#| label: tbl-wbl

read_excel("/Users/fsolt/Documents/Projects/gender_equality/paper/policy_adoption/data-raw/wbl2024_v1.xlsx",
           sheet = "WBL Panel 2024") %>% 
  names() %>% 
  `[`(8:55) %>% 
  as_tibble() %>% 
  filter(!str_detect(value, "^Length|[Dd]ays")) %>% 
  mutate(Indicator = if_else(str_detect(value, "[A-Z]{2,}"), value, NA_character_) %>% 
           str_replace("EURSHIP", "EUR-\nSHIP"),
         Laws = if_else(str_detect(value, "[A-Z][a-z]"), value, NA_character_),
         count_i = cumsum(!is.na(Indicator)),
         Indicator = if_else(!is.na(Indicator),
                             paste0(count_i, ". ", Indicator),
                             NA_character_)) %>% 
  fill(Indicator) %>% 
  group_by(Indicator) %>% 
  mutate(count_lp = row_number() - 1,
         Laws = if_else(!is.na(Laws),
                        paste0(count_lp, ". ", Laws),
                        "")) %>% 
  ungroup() %>% 
  mutate(Indicator = if_else(!Indicator==lag(Indicator) | row_number()==1,
                             Indicator,
                             ""),
         Laws = lead(Laws)) %>%
  select(Indicator, Laws) %>% 
  rename(Topic = Indicator) %>% 
  filter(!Laws=="") %>% 
  modelsummary::datasummary_df(title = "WBL Policy Index",
                               longtable = TRUE, 
                               output = "kableExtra",
                               notes = c("Source: Women, Business, and the Law Database v1.0 2024 (World Bank 2024).")) %>%
  kableExtra::kable_styling(font_size = 10) %>%
  kableExtra::column_spec(1, width = "10em") %>%
  kableExtra::column_spec(2, width = "20em")
```

```{r wblplot, fig.cap="The WBL Policy Index in the OECD", fig.height = 9, fig.width = 7.5}
#| label: fig-wblplot

wbl_data %>%
  group_by(country) %>%
  mutate(last_wbl = last(wbl, na_rm = TRUE)) %>% 
  ggplot(aes(x = year, y = wbl)) +
  geom_line(linetype = "dotted") +
  geom_line(aes(y = wbl_included)) +
  theme_bw() +
  theme(legend.position = "none") +
  coord_cartesian(ylim = c(40, 100)) +
  labs(x = NULL, y = "WBL Policy Index") +
  facet_wrap(~reorder(country, -last_wbl), ncol = 6) +
  theme(axis.text.x  = element_text(size = 7,
                                    angle = 90,
                                    vjust = .45,
                                    hjust = .95),
        strip.text.x = element_text(size = 8),
        strip.background = element_rect(fill = "white", colour = "white"),
        plot.title = element_text(size=8)) +
  plot_annotation(caption = str_wrap("Source: World Bank (2024).", 85))
```

@fig-wblplot depicts the trends in the WBL policy index in the thirty-eight countries of the OECD from 1970, the first year included in the WBL database, through 2023, when the time series end.
A half-century ago, policy in many countries did little to advance gender equality in paid employment and much to stand in its way: the only WBL policy adopted in all of these countries was that women could travel internationally in the same way as men.
At that time Denmark and Sweden had the highest scores on the index, having already adopted twenty-five of the thirty-five policies advancing gender equality in access to employment and entrepreneurship, but neither had passed such crucial policies as prohibiting discrimination in employment based on gender or addressing and penalizing sexual harassment at work and domestic violence at home.
More recently, twelve OECD member states have adopted every one of the policies listed in @tbl-wbl and so reached a score of 100 on the index: Belgium was the first to do so, in 2010, and the Netherlands the last of these twelve, in 2022.
In 2023, even the lowest-scoring OECD countries---Israel, Chile, and Japan, each with an 80 on the WBL policy index---had adopted more equality-enhancing policies than the highest-scoring countries had five decades earlier. 
Over the countries and years we analyze here, gender equality policymaking progressed the most in Latvia and Estonia, where the WBL index increased by over 40 points, and the least in Canada, where only two additional policies were adopted, and in Costa Rica, where just one was.
Both the extent to which these countries have passed these laws and the pace at which they have done so varies considerably.


### Substantive Representation in Policies Advancing Workplace Gender Equality

Our first question is whether growing gender egalitarianism among citizens prompts their representatives to adopt policies that enhance gender equality in employment.
As can be seen in @fig-wbl-corr, the correlation between macroegalitarianism and the WBL policy index is very strong.

```{r wblplot, fig.cap="Macroegalitarianism and Policies Advancing Gender Equality in Employment in the OECD", fig.height = 7, fig.width = 7.5}
#| label: fig-wbl-corr
pge <- rio::import(here("data",
                        "pge.rda"))

wbl_pge <- pge %>% 
  group_by(draw) %>% 
  group_split() %>% 
  map(. %>% 
        group_by(country) %>% 
        mutate(pge = pge*100) %>%
        ungroup() %>% 
        inner_join(wbl_data %>% 
                     select(country, year, wbl_index),
                   by = c("country", "year")))

wbl_cor <- map(wbl_pge,
              ~ with(.x,
                     cor(pge, wbl_index,
                         use = "pairwise.complete.obs"))) %>% 
  unlist() %>% 
  mean() %>% 
  round(2) %>% 
  sprintf("%.2f", .) %>% 
  paste0("R = ", .)

wbl_label <- tibble(pge_lag = 90,
                         wbl_index = 44,
                         label = wbl_cor)

wbl_plot <- ggplot(wbl_data,
                  aes(x = pge_lag,
                      y = wbl_index)) +
  geom_segment(aes(x = pge_lag-1.96*pge_se_lag, xend = pge_lag+1.96*pge_se_lag,
                   y = wbl_index, yend = wbl_index),
               na.rm = TRUE,
               alpha = .06) +
  geom_point(alpha = .12) +
  geom_smooth(method = 'lm', se = FALSE) +
  theme_bw() +
  theme(legend.position="none",
        axis.text  = element_text(size=10),
        axis.title = element_text(size=12)) +
  scale_x_continuous(limits=c(25, 100),
                     breaks=seq(25, 100, by = 25)) +
  scale_y_continuous(limits=c(40, 100)) +
  labs(x = TeX("Macroegalitarianism$_{t-1}$"), y = "WBL Policy Index") +
  geom_label(data = wbl_label, aes(label = label))

wbl_plot
```

Researchers are wary of drawing conclusions based on such correlations, however.
This strong bivariate relationship may be the consequence of spuriousness.
@Kim2022, for example, finds that gains in women's descriptive representation predict subsequent increases in the WBL policy index, especially in democratic countries.
As we have seen in @fig-m3-wr in the last chapter and @fig-m2-nq in this one, gains in women's descriptive representation also yield higher macroegalitarianism in the democracies of the OECD.
The apparent relationship between gender egalitarianism among a country's citizens and the adoption of policies increasing gender equality may be driven entirely by women in the legislature---or some other variable, like national legislative quotas [see @Weeks2022]---causing both.

So we again construct a model that includes our usual suspects of such spuriousness: national quotas, women's descriptive representation, feminist movement strength, and the presence of party lists in the electoral system, each measured as in our previous analyses.
And, also as before, we use the within-between specification to parse out cross-country differences from over-time trends in each of our variables [see @Bell2015] in a Bayesian multilevel model with varying intercepts for both countries and years that capture the distinctive time-invariant characteristics of each country and the global time-varying traits that affected all countries at once [see @Shor2007]. 
Consistent with our now-familar approach, we also include as a predictor the one-year lag of the WBL policy index to capture the dynamics of policy adoption [see @Keele2006] and the measurement uncertainty in the PGE scores [see @Tai2024].

```{r wbl_b}
if (!file.exists(file.path(policy_path,
                           "data",
                           "wbl_results.rda"))) {
  
  wbl_data2 <- wbl_data %>% 
    filter(!is.na(wbl)) %>% 
    group_by(country) %>% 
    transmute(year,
              wbl,
              wbl_lag = lag(wbl), # previous year
              wbl_mean = mean(wbl_lag, na.rm = TRUE),
              wbl_diff = wbl_lag - wbl_mean,
              women_rep,
              women_rep_lag = lag(women_rep), # previous year
              women_rep_mean = mean(women_rep, na.rm = TRUE),
              women_rep_diff = women_rep - women_rep_mean,
              pge,
              pge_se,
              pge_lag, # previous year
              pge_se_lag, # previous year
              pge_mean = mean(pge_lag, na.rm = TRUE),
              pge_mean_se = sqrt(sum(pge_se_lag^2, na.rm = TRUE))/
                length(pge),
              pge_diff = pge_lag - pge_mean,
              pge_diff_se = sqrt(pge_se_lag^2 + pge_mean_se^2)/2,
              fmi,
              fmi_mean = mean(fmi, na.rm = TRUE),
              fmi_diff = fmi - fmi_mean,
              national_quota,
              national_quota_mean = mean(national_quota),
              national_quota_diff = national_quota - national_quota_mean,
              list,
              list_mean = mean(list, na.rm = TRUE),
              list_diff = list - list_mean,
              gdppc,
              gdppc_mean = mean(gdppc, na.rm = TRUE),
              gdppc_diff = gdppc - gdppc_mean) %>% 
    ungroup() %>% 
    filter(., complete.cases(.))
  
  bf_wbl <- bf(wbl ~ 
                 me(pge_diff, pge_diff_se) +
                 me(pge_mean, pge_mean_se) +
                 women_rep_diff +
                 women_rep_mean +
                 fmi_diff +
                 fmi_mean +
                 national_quota_diff +
                 national_quota_mean +
                 gdppc_diff +
                 gdppc_mean +
                 wbl_lag +
                 (1|c|country) + (1|t|year))

  m1_wbl_b <- brm(formula = bf_wbl,  
                  data = wbl_data2,
                  backend = "cmdstanr",
                  control=list(adapt_delta = 0.99, 
                               max_treedepth = 14),
                  warmup = 500, 
                  iter = 1000, 
                  chains = 4, 
                  cores = 4,
                  seed = 324)
  
  m1_data <- m1_wbl_b$data
  
  m1_data_2sd <- m1_data %>% 
    select(pge_diff,
           pge_mean,
           women_rep_diff,
           women_rep_mean,
           fmi_diff,
           fmi_mean,
           national_quota_mean,
           national_quota_diff,
           gdppc_mean,
           gdppc_diff,
           wbl_lag) %>% 
    summarize(across(everything(), by2sd)) %>% 
    pivot_longer(everything()) %>% 
    mutate(`.variable` = case_when(name == "pge_mean" ~ 
                                     "bsp_mepge_meanpge_mean_se",
                                   name == "pge_diff" ~
                                     "bsp_mepge_diffpge_diff_se",
                                   TRUE ~ paste0("b_", name)),
           var_names = c("Macroegalitarianism, Difference",
                         "Macroegalitarianism, Mean",
                         "Descriptive Representation, Difference",
                         "Descriptive Representation, Mean",
                         "Feminist Movement Strength, Difference",
                         "Feminist Movement Strength, Mean",
                         "National Quota, Difference",
                         "National Quota, Mean",
                         "GDP per Capita, Difference",
                         "GDP per Capita, Mean",
                         "Lagged WBL Policy Index"),
           sd2 = ifelse(str_detect(.variable, "list_|fmi_diff|_lag"),
                        1,
                        value))
  
  coef_data0_m1 <- m1_wbl_b %>% 
    as_draws_df() %>% 
    tidybayes::gather_draws(`bs?p?_.*`, regex = TRUE) %>% 
    filter(!str_detect(`.variable`, "_Intercept")) %>% 
    left_join(m1_data_2sd, by = join_by(.variable))
  
  cy_summary_m1 <- m1_data %>%
    count(country) %>%
    pull(n) %>%
    summary()
  
  save(wbl_data2, 
       file = file.path(policy_path,
                        "data",
                        "wbl_data2.rda"))
  
  save(m1_data, m1_data_2sd, coef_data0_m1, cy_summary_m1, 
       file = file.path(policy_path,
                        "data",
                        "wbl_results.rda"))
} else {
  load(file = file.path(policy_path, "data", "wbl_data2.rda"))
  load(file = file.path(policy_path, "data", "wbl_results.rda"))
}
```

```{r m1wblplot, fig.cap="Predicting the WBL Policy Index in OECD Countries \\label{m1_wbl_plot}", fig.height = 7, fig.width = 7.5}
#| label: fig-m1-wbl
ordered <- c("Macroegalitarianism, Difference",
             "Macroegalitarianism, Mean", 
             "Descriptive Representation, Difference",
             "Descriptive Representation, Mean",
             "Feminist Movement Strength, Difference",
             "Feminist Movement Strength, Mean", 
             "National Quota, Difference",
             "National Quota, Mean",
             "GDP per Capita, Difference",
             "GDP per Capita, Mean",
             "Lagged WBL Index") %>% 
  rev()

coef_data_m1 <- coef_data0_m1 %>% 
  mutate(std_coef = round(.value * sd2, 1),
         term = factor(var_names, levels = ordered)) %>%
  ggdist::median_qi(std_coef, .width = c(.8, .9)) %>%
  mutate(ci = paste0(round(.lower, 1), " to ", round(.upper, 1))) %>%
  left_join(m1_data_2sd, ., by = join_by(.variable))

coef_data_m1_total <- coef_data0_m1 %>% 
  group_by(.chain, .iteration, .draw) %>% 
  mutate(alpha = mean(ifelse(name=="wbl_lag", .value, NA_real_),
                      na.rm = TRUE)) %>% 
  ungroup() %>% 
  group_by(.variable) %>% 
  mutate(std_coef0 = round(.value * sd2, 1),
         std_coef = round(std_coef0/(1 - alpha), 1),
         term = factor(var_names, levels = ordered)) %>%
  ggdist::median_qi(std_coef, .width = c(.8, .9)) %>%
  mutate(ci = paste0(round(.lower, 1), " to ", round(.upper, 1))) %>%
  left_join(m1_data_2sd, ., by = join_by(.variable))

coef_plot_m1 <- coef_data0_m1 %>% 
  mutate(std_coef = .value * sd2,
         term = factor(var_names, levels = ordered)) %>% 
  filter(!str_detect(var_names, "Lagged")) %>% 
  ggplot(aes(y = term, x = std_coef)) +
  ggdist::stat_halfeye(.width = .8,
                       fill = "grey60",
                       linewidth = 2) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  theme_light() +
  xlab("Standardized Coefficients") +
  ylab(NULL) 

lag_plot_m1 <- coef_data0_m1 %>% 
  mutate(std_coef = .value * sd2,
         term = factor(var_names, levels = ordered)) %>% 
  filter(str_detect(var_names, "Lagged")) %>% 
  mutate(term = "Lagged Enrollment") %>% 
  ggplot(aes(y = term, x = std_coef)) +
  ggdist::stat_halfeye(.width = .8,
                       fill = "grey60",
                       linewidth = 2) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  theme_light() +
  theme(strip.text.x = element_blank(),
        strip.background = element_blank()) +
  xlab("Unstandardized Coefficient") +
  ylab(NULL)

coef_plot_m1 + lag_plot_m1 +
  plot_layout(ncol = 1, widths = c(1, 1), heights = c(7, 1)) +
  plot_annotation(caption = "Notes: Dots indicate posterior medians; whiskers describe 80% credible\nintervals; shading depicts the posterior probability distribution.")
```

The results are displayed in @fig-m1-wbl.
The are, perhaps, surprising.
Even with OECD, a group of relatively high-income countries, the richer countries score higher on the WBL policy index than the poorer ones, by `r get_coef("gdppc_mean", coef_data_m1)` points immediately, and due to the strong dynamics in the adoption of these policies, `r get_coef("gdppc_mean", coef_data_m1_total)` points over time.
This may indicate a long-term causal influence, but gains in GDP per capita do not evidence a similar effect so we are careful to not draw strong conclusions.

National gender quotas bear little relationship to the adoption of these equality-enhancing policies in this model.
Nor does the average strength of the feminist movement, but _gains_ in the Feminist Movement Index increase the adoption of these policies by `r get_coef("fmi_diff", coef_data_m1)` points in the short run and `r get_coef("fmi_diff", coef_data_m1_total)` points compounded over time.

We turn then to the model's estimates of the coefficients for macroegalitarianism on policies advancing gender equality in employment, first considering cross-country differences.
A two-standard-deviation difference in PGE scores is found to correspond to an immediate `r get_coef("pge_mean", coef_data_m1)` point difference in the WBL policy index, which grows to `r get_coef("pge_mean", coef_data_m1_total)` points when the dynamics of the index are taken into account.
The posterior distribution indicates that the probability that this estimate is positive is `r {{coef_data0_m1 %>% filter(name == "pge_mean" & .value > 0) %>% nrow()}/20} %>% round()`%.
Again, we treat this result cautiously: it may reflect how public opinion influences policymakers over the long term, but it may also be the product of differences across countries that remain outside of our model.

We put more weight on how year-to-year changes in macroegalitarianism correspond to subsequent changes in policy.
These are not perfect for the purpose of drawing conclusions about causation, but given that the attitudes of the public are not subject to experimental manipulation, they are the strongest evidence available.
And, in this case, the evidence is indeed strong.
A two-standard-deviation increase in macroegalitarianism in one year within a country is estimated to be followed by a `r get_coef("pge_diff", coef_data_m1)` gain in the WBL policy index in the next.
Over time, as past policymaking influences future policymaking, this gain increases to `r get_coef("pge_diff", coef_data_m1_total)` points.
Just as the models earlier in this chapter indicated that more gender egalitarian public opinion spurs legislators to adopt and raise national gender quotas to advance gender equality in politics, this model indicates that it also induces them to adopt policies advancing gender equality in employment.


### Public Responsiveness to Policies Advancing Workplace Gender Equality

That governments respond to gender egalitarianism in the public with policies addressing equality in both politics and work does not necessarily suggest that the public reacts to these policies similarly.
That is, even though the public reacts to the election of more women and the adoption of legislative gender quotas by becoming even more egalitarian, it could be that its reaction is different to policies removing barriers to equality in employment.
After all, these policies intrude more directly into people's daily lives than the makeup of the legislature does.
It would not be too surprising if these more intrusive policies, rather than working to create their own constituencies, instead prompt a thermostatic backlash.

```{r wblsem_results}    
if (!file.exists(file.path(policy_path, "data", "wblsem_results.rda"))) {  
  bf_pge <- bf(pge ~ 
                 wbl_diff +
                 wbl_mean +
                 women_rep_diff +
                 women_rep_mean +
                 fmi_diff +
                 fmi_mean +
                 national_quota_diff +
                 national_quota_mean +
                 gdppc_diff +
                 gdppc_mean +
                 pge_lag +
                 (1|c|country) + (1|t|year))

  m2_wblsem_b <- brm(formula = bf_wbl + 
                      bf_pge + 
                      set_rescor(TRUE),  
                    data = wbl_data2,
                    backend = "cmdstanr",
                    control=list(adapt_delta = 0.99, 
                                 max_treedepth = 14),
                    warmup = 500, 
                    iter = 1000, 
                    chains = 4, 
                    cores = 4,
                    seed = 324)
  
  m2_data <- m2_wblsem_b$data
  
  m2_data_2sd <- m2_data %>% 
    select(pge_diff,
           pge_mean,
           women_rep_diff,
           women_rep_mean,
           fmi_diff,
           fmi_mean,
           national_quota_mean,
           national_quota_diff,
           gdppc_mean,
           gdppc_diff,
           wbl_lag) %>% 
    summarize(across(everything(), by2sd)) %>% 
    pivot_longer(everything()) %>% 
    mutate(`.variable` = case_when(name == "pge_mean" ~ 
                                     "bsp_wbl_mepge_meanpge_mean_se",
                                   name == "pge_diff" ~
                                     "bsp_wbl_mepge_diffpge_diff_se",
                                   TRUE ~ paste0("b_wbl_", name)),
           var_names = c("Macroegalitarianism, Difference",
                         "Macroegalitarianism, Mean",
                         "Descriptive Representation, Difference",
                         "Descriptive Representation, Mean",
                         "Feminist Movement Index, Difference",
                         "Feminist Movement Index, Mean",
                         "National Quota, Difference",
                         "National Quota, Mean",
                         "GDP per Capita, Difference",
                         "GDP per Capita, Mean",
                         "Lagged WBL Policy Index"
           ),
           sd2 = ifelse(str_detect(.variable, "list_|_lag"),
                        1,
                        value),
           dv = "WBL Policy Index") %>% 
    bind_rows(m2_data %>% 
                select(wbl_diff,
                       wbl_mean,
                       women_rep_diff,
                       women_rep_mean,
                       fmi_diff,
                       fmi_mean,
                       national_quota_mean,
                       national_quota_diff,
                       gdppc_mean,
                       gdppc_diff,
                       pge_lag) %>% 
                summarize(across(everything(), by2sd)) %>% 
                pivot_longer(everything()) %>% 
                mutate(`.variable` = paste0("b_pge_", name),
                       var_names = c("WBL Policy Index, Difference",
                                     "WBL Policy Index, Mean",
                                     "Descriptive Representation, Difference",
                                     "Descriptive Representation, Mean",
                                     "Feminist Movement Index, Difference",
                                     "Feminist Movement Index, Mean",
                                     "National Quota, Difference",
                                     "National Quota, Mean",
                                     "GDP per Capita, Difference",
                                     "GDP per Capita, Mean",
                                     "Lagged Macroegalitarianism"
                       ),
                       sd2 = ifelse(str_detect(.variable, "list_|_lag"),
                                    1,
                                    value),
                       dv = "Macroegalitarianism")) %>% 
    mutate(dv = factor(dv, levels = c("WBL Policy Index",
                                      "Macroegalitarianism")))
  
  coef_data0_wblsem <- m2_wblsem_b %>% 
    as_draws_df() %>% 
    tidybayes::gather_draws(`bs?p?_.*`, regex = TRUE) %>% 
    filter(!str_detect(`.variable`, "_Intercept")) %>% 
    left_join(m2_data_2sd, by = join_by(.variable))
  
  save(m2_data, m2_data_2sd, coef_data0_wblsem, 
       file = file.path(policy_path,
                        "data",
                        "wblsem_results.rda"))
} else {
  load(file = file.path(policy_path, "data", "wblsem_results.rda"))
}
```

```{r m2wblplot, fig.cap="Predicting the WBL Policy Index and Macroegalitarianism in OECD Countries", fig.height = 9, fig.width = 7.5}
#| label: fig-m2-wbl

ordered_wblsem <- c("Macroegalitarianism, Difference",
                    "Macroegalitarianism, Mean", 
                    "WBL Policy Index, Difference",
                    "WBL Policy Index, Mean",
                    "Descriptive Representation, Difference",
                    "Descriptive Representation, Mean",
                    "Feminist Movement Index, Difference",
                    "Feminist Movement Index, Mean",
                    "National Quota, Difference",
                    "National Quota, Mean",
                    "GDP per Capita, Difference",
                    "GDP per Capita, Mean",
                    "Lagged WBL Policy Index",
                    "Lagged Macroegalitarianism") %>% 
  rev()

coef_data_wblsem <- coef_data0_wblsem %>% 
  mutate(std_coef = round(.value * sd2, 2),
         term = factor(var_names, levels = ordered_wblsem)) %>%
  ggdist::median_qi(std_coef, .width = c(.8, .9)) %>%
  mutate(ci = paste0(round(.lower, 1), " to ", round(.upper, 1))) %>%
  left_join(m2_data_2sd, ., by = join_by(.variable))

coef_data_wblsem_total <- coef_data0_wblsem %>%  
  group_by(.chain, .iteration, .draw) %>% 
  mutate(alpha_wbl = mean(ifelse(name=="wbl_lag", .value, NA_real_),
                         na.rm = TRUE),
         alpha_pge = mean(ifelse(name=="pge_lag", .value, NA_real_),
                          na.rm = TRUE)) %>% 
  ungroup() %>% 
  group_by(.variable) %>% 
  mutate(std_coef0 = round(.value * sd2, 1),
         std_coef = if_else(dv == "WBL Policy Index",
                            round(std_coef0/(1 - alpha_wbl), 1),
                            round(std_coef0/(1 - alpha_pge), 1)),
         term = factor(var_names, levels = ordered_wblsem)) %>%
  ggdist::median_qi(std_coef, .width = c(.8, .9)) %>%
  mutate(ci = paste0(round(.lower, 1), " to ", round(.upper, 1))) %>%
  right_join(m2_data_2sd, by = join_by(.variable))

coef_plots_wblsem <- coef_data0_wblsem %>% 
  mutate(std_coef = .value * sd2,
         term = factor(var_names, levels = ordered_wblsem)) %>% 
  filter(!str_detect(var_names, "Lagged")) %>% 
  ggplot(aes(y = term, x = std_coef)) +
  ggdist::stat_halfeye(.width = .8,
                       fill = "grey60",
                       linewidth = 2) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  facet_grid(~ dv) +
  theme_light() +
  theme(strip.text.x = element_text(size = 10, color = "black"),
        strip.background = element_rect(fill = "white", colour = "white")) +
  xlab("Standardized Coefficients") +
  ylab(NULL)

lag_plots_wblsem <- coef_data0_wblsem %>% 
  mutate(std_coef = .value * sd2,
         term = factor(var_names, levels = ordered_wblsem)) %>% 
  filter(str_detect(var_names, "Lagged")) %>% 
  mutate(term = "Lagged Response Variable") %>% 
  ggplot(aes(y = term, x = std_coef)) +
  ggdist::stat_halfeye(.width = .8,
                       fill = "grey60",
                       linewidth = 2) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  facet_grid(~ dv) +
  theme_light() +
  theme(strip.text.x = element_blank(),
        strip.background = element_blank()) +
  xlab("Unstandardized Coefficients") +
  ylab(NULL) 

coef_plots_wblsem + lag_plots_wblsem +
  plot_layout(ncol = 1, widths = c(1, 1), heights = c(9, 1)) +
  plot_annotation(caption = "Notes: Dots indicate posterior medians; whiskers describe 80% credible\nintervals; shading depicts the posterior probability distribution.")
```

We test this possibility with a simultaneous-equations model similar to those we have used previously, predicting at once both the WBL index of gender-equality-enhancing policies and the PGE scores of macroegalitarianism.
@fig-m2-wbl depicts the results.
The left side of the plot reproduces the findings of @fig-m1-wbl, again providing reassurance that our specification of that model successfully avoided any bias due to endogeneity.

The figure's right side shows the model's estimates for macroegalitarianism.
These estimates provide no evidence of a thermostatic effect of increasingly gender-equal policies toward work on public opinion; there is no backlash.
Instead, increases in the WBL policy index are followed by increases in public egalitarianism.
A two-standard-deviation gain in the former yields an immedidate `r get_coef("pge_diff", coef_data_wblsem) %>% str_replace("\\.(\\d)\\d", ".\\1")` point gain in the latter, and this gain expands to `r get_coef("pge_diff", coef_data_wblsem_total)` points over time.


### A Further Test: Childcare Provision

One known shortcoming of the longitudinal WBL data we use here is its exclusion of the single policy most often and closely tied to gender equality in the workforce: childcare.
In 2024, the World Bank revised the WBL index to include childcare policy for the first time.
Version 2.0 of the WBL dataset includes data on whether there are laws that establish public and private center-based childcare services as well as laws establishing employer-provided childcare.^[
The new version also highlights the importance of gender-based violence to gender equality in the workplace, moving and expanding its treatment of laws combating sexual harassment from the Workplace indicator and provisions addressing domestic violence from the Marriage indicator, along with information about laws banning child marriage and criminalizing femicide, to a new Safety indicator [see @WorldBank2024a, 25-27].  As the WBL index v1.0 does include some information on policies addressing gender-based violence, we leave a more focused analysis of these specific policies to future work.]
Unfortunately, this newly revised and expanded WBL index is currently available only for a single year.
That renders it unsuitable for our purposes for two reasons.
Most importantly, the cross-sectional nature of these data prevent the time-sensitive dynamic analyses that we employ to convincingly test the representation of public opinion and the responsiveness of the public to policy change across the high-income democracies of the OECD.
But also, as a practical matter, the PGE data as yet extends to within a year of the updated WBL in only two of the thirty-eight countries in our sample.
This makes even a cross-sectional analysis unfeasible.
We must look elsewhere for data on childcare policy.

Childcare policy is multifaceted, with many potential levers for affecting cost, availability, and quality [@Hegewisch2011, 128-129].^[
The availability of childcare is seen the most important indicator of policy effort---and more predictive of women's opportunities for employment---than government expenditures and childcare costs [@Hegewisch2011, 128-129].
In any event, the available expenditures data has validity problems because the it covers older preschool children, whose often 'short-hour' care is associated with more part-time employment among mothers [see, e.g., @Korpi2000, 145].]
We therefore consider childcare enrollments, which are an indicator of all three of these aspects of policy.
Further, as a policy outcome can also be seen to complement our earlier focus on policy outputs in the WBL policy index.
To provide a measure across our countries of interest, we look to OECD data on enrollments in early childhood education and care among the very young, children aged zero to two [@OECD2024].

@fig-enrplot shows how these enrollments have varied across countries and over time.
The highest rates are found in the Netherlands in 2020, where nearly 70% of children under the age of two were enrolled in nursuries, day care centers, and the like.
Center-based care for very young children was almost vanishingly rare in Slovakia and Turkey, on the other hand.
Beyond the differences in levels and trends across countries, the plot reveals that these data are more sparse than others we have considered, covering less than half of the country-years in the OECD from 1999 to 2020.
While the data include long time-series for many countries, observations are rarer for many others, and for Canada there are no observations at all.
Still, an analysis of these data seems a worthwhile check on the conclusions reached by our examination of the WBL policy index.

```{r ecec_data}
if (!file.exists(file.path(policy_path, "data-raw", "ecec_data.csv"))) {
  download.file("https://web.archive.org/web/20240718100341/http://www.oecd.org/els/soc/PF3_2_Enrolment_childcare_preschool.xlsx",
                file.path(policy_path, "data-raw", "oecd_pf3_2.xlsx"))
  
  ecec_data <- read_excel(file.path(policy_path, "data-raw", "oecd_pf3_2.xlsx"),
                          sheet = "Enrolment_0-2-year-olds",
                          skip = 5) %>% 
    mutate(country = countrycode(...1, "iso3c", "country.name",
                                 warn = FALSE)) %>% 
    filter(!is.na(country)) %>% 
    pivot_longer(cols = matches("\\d{4}"),
                 names_to = "year",
                 names_transform = list(year = as.integer),
                 values_to = "ecec_enrollment",
                 values_transform = list(ecec_enrollment = as.numeric)) %>% 
    select(country, year, ecec_enrollment)
  
  write_csv(ecec_data, file.path(policy_path, "data-raw", "ecec_data.csv"))
} else {
  ecec_data <- read_csv(file.path(policy_path, "data-raw", "ecec_data.csv"),
                        col_types = "cddd")  
}

if (!file.exists(file.path(policy_path, "data-raw", "ecec_data1.rda"))) {
  control_files <- c("qarot.rda", "des.rda", "fmi.rda", "gdppc.rda")
  
  walk(control_files, \(f) 
       load(file.path(descrep_path, "data-raw", f), .GlobalEnv))
 
  pge_summary <- rio::import(here("data",
                                  "pge_summary.rda")) %>% 
    mutate(across(starts_with("p"),
                  ~ .x * 100,
                  .names = "{.col}"))
  
  ecec_data1 <- pge_summary %>% 
    filter(year >= 1999) %>% 
    select(country, year, pge, pge_se) %>% 
    full_join(ecec_data,
              by = c("country", "year")) %>%
    left_join(qarot,
              by = c("country" = "countryname", "year")) %>% 
    left_join(des,
              by = c("country" ="countryname", "year")) %>%
    left_join(fmi,
              by = c("country", "year")) %>% 
    group_by(country) %>% 
    mutate(countryname = country,
           iso2c = countrycode::countrycode(country, 
                                            "country.name",
                                            "iso2c",
                                            warn = FALSE),
           pge_lag = lag(pge),
           pge_se_lag = lag(pge_se),
           ecec_enr = zoo::na.approx(ecec_enrollment, na.rm = FALSE),
           ecec_enr_lag = lag(ecec_enr),
           fmi = if_else(country == "United States" & year < 1975, 3, fmi),
           women_rep_included = ifelse(!is.na(lag(pge)),
                                       women_rep,
                                       NA_real_),
           national_quota = if_else(is.na(defacto_threshold), 0,
                                    defacto_threshold)) %>% 
    filter(countryname %in% oecd_countries) %>%
    left_join(gdppc, by = c("country", "year")) %>% 
    mutate(gdppc = gdppc/10000) %>% 
    fill(list) %>% 
    ungroup() %>% 
    arrange(country, year)
  
  save(ecec_data1, file = file.path(policy_path, "data-raw", "ecec_data1.rda"))
} else {
  pge_summary <- rio::import(here("data",
                                  "pge_summary.rda")) %>% 
    mutate(across(starts_with("p"),
                  ~ .x * 100,
                  .names = "{.col}"))
  
  ecec_data1 <- rio::import(file.path(policy_path,
                                      "data-raw", 
                                      "ecec_data1.rda"))
}
```

```{r enrplot, fig.cap="Enrollment in Early Childhood Education and Care, Ages 0-2, in the OECD", fig.height = 9, fig.width = 7.5}
#| label: fig-enrplot

ecec_data1 %>%
  group_by(country) %>%
  mutate(last_enr = last(ecec_enrollment, na_rm = TRUE),
         enr_solo = if_else(is.na(lag(ecec_enrollment)) &
                                 is.na(lead(ecec_enrollment)) &
                                 !is.na(ecec_enrollment),
                            ecec_enrollment,
                            NA_real_)) %>% 
  ggplot(aes(x = year)) +
  geom_line(aes(y = ecec_enrollment)) +
  geom_point(aes(y = enr_solo), size = .1) +
  theme_bw() +
  theme(legend.position = "none") +
  coord_cartesian(xlim = c(1999, 2022)) +
  labs(x = NULL, y = "Enrollment") +
  facet_wrap(~reorder(country, -last_enr), ncol = 6) +
  theme(axis.text.x  = element_text(size = 7,
                                    angle = 90,
                                    vjust = .45,
                                    hjust = .95),
        strip.text.x = element_text(size = 8),
        strip.background = element_rect(fill = "white", colour = "white"),
        plot.title = element_text(size=8)) +
  plot_annotation(caption = str_wrap("Source: OECD (2024).", 85))
```

```{r ececenrplot, fig.cap="Macroegalitarianism and Enrollment in Early Childhood Education and Care, Ages 0-2, in OECD Countries", fig.height = 9, fig.width = 7.5}
#| label: fig-ecec-enrplot

pge <- rio::import(here("data",
                        "pge.rda"))

ecec_pge <- pge %>% 
  group_by(draw) %>% 
  group_split() %>% 
  map(. %>% 
        group_by(country) %>% 
        mutate(pge = pge*100) %>%
        ungroup() %>% 
        inner_join(ecec_data,
                   by = c("country", "year")))

ecec_enr_cor <- map(ecec_pge,
                    ~ with(.x, cor(pge, ecec_enrollment,
                                   use = "pairwise.complete.obs"))) %>% 
  unlist() %>% 
  mean() %>% 
  round(2) %>% 
  sprintf("%.2f", .) %>% 
  paste0("R = ", .)

ecec_enr_label <- tibble(pge = 90, 
                         ecec_enrollment = 4,
                         label = ecec_enr_cor)

ecec_enr_plot <- ggplot(ecec_data1 %>% filter(!is.na(ecec_enrollment)),
                        aes(x = pge,
                            y = ecec_enrollment)) +
  geom_segment(aes(x = pge - 1.96*pge_se, xend = pge + 1.96*pge_se,
                   y = ecec_enrollment, yend = ecec_enrollment),
               na.rm = TRUE,
               alpha = .1) +
  geom_text(aes(label = iso2c), size = 2) +
  geom_smooth(method = 'lm', se = FALSE) +
  theme_bw() +
  theme(legend.position="none",
        axis.text  = element_text(size=10),
        axis.title = element_text(size=12)) +
  scale_x_continuous(limits=c(40, 100),
                     breaks=seq(40, 100, by = 20)) +
  labs(x = "Macroegalitarianism", y = "Enrollment in Early Childhood\n Education and Care, Ages 0-2") +
  geom_label(data = ecec_enr_label, aes(label = label)) +
  plot_annotation(caption = "Notes: Whiskers describe 80% credible intervals.")
  
ecec_enr_plot
```

@fig-ecec-enrplot shows the bivariate relationship between gender egalitarianism and these very early childhood enrollments.
Enrollment rates in education and care for children aged zero to two are plotted vertically on the y-axis, and PGE scores are plotted horizontally on the x-axis; the horizontal whiskers trace the 80% credible intervals of the PGE scores.
The relationship between these two variables is positive and strong: the bivariate correlation, with the uncertainty in the PGE scores taken into account, is `r ecec_enr_cor %>% str_extract("\\.\\d{2}")`.
Still, a strong correlation is famously insufficient to establish causation.
A strong correlation may instead, for example, simply arise due to spuriousness; that is, egalitarian attitudes and early childhood care enrollments may both be driven by some third factor, such as levels of women's descriptive representation.
We need a more sophisticated model to draw firmer conclusions. 

First, as ever, we need to account for likely sources of spuriousness.
Levels of descriptive representation and the strength of the feminist movement are two variables that plausibly could influence both the public's gender egalitarian attitudes and the constellation of policies that shape the rate of young children's enrollment in education and care.
@Weeks2022 finds that national quota adoption worked to shift family policies in the direction of more gender equality among twenty OECD democracies, so taking this factor into consideration is also important.
Richer and growing economies may also be expected to be better able to afford to make childcare available, so we include GDP per capita as a control as well.

To model enrollment in early childhood education and care, we use now-familiar tools. 
We again use a Bayesian multilevel model that includes varying intercepts for 
each country and each year that capture any distinctive differences across space and any shocks that occur over time and so minimize bias due to heteroskedasticity or from variables omitted from the model [see @Shor2007].
We use the 'within-between specification' to separate time-varying predictors into their mean values for each country and the changes over time, with the latter providing the best evidence of causation [see @Bell2015].
And we of course incorporate the measurement uncertainty in the PGE scores into our model [see @Tai2024].
Finally, because past rates of early childcare enrollment should be expected to predict current values, we treat the process as dynamic and include the rate of enrollment in the previous year as a predictor.

```{r enr_b}
if (!file.exists(file.path(policy_path,
                           "data",
                           "enr_results.rda"))) {
  ecec_enr_data2 <- ecec_data1 %>% 
    filter(!is.na(ecec_enrollment)) %>% 
    group_by(country) %>% 
    transmute(year,
              ecec_enr,
              ecec_enr_lag, # previous year
              ecec_enr_mean = mean(ecec_enr_lag, na.rm = TRUE),
              ecec_enr_diff = ecec_enr_lag - ecec_enr_mean,
              women_rep,
              women_rep_lag = lag(women_rep), # previous year
              women_rep_mean = mean(women_rep, na.rm = TRUE),
              women_rep_diff = women_rep - women_rep_mean,
              pge,
              pge_se,
              pge_lag, # previous year
              pge_se_lag, # previous year
              pge_mean = mean(pge_lag, na.rm = TRUE),
              pge_mean_se = sqrt(sum(pge_se_lag^2, na.rm = TRUE))/
                length(pge),
              pge_diff = pge_lag - pge_mean,
              pge_diff_se = sqrt(pge_se_lag^2 + pge_mean_se^2)/2,
              fmi,
              fmi_mean = mean(fmi, na.rm = TRUE),
              fmi_diff = fmi - fmi_mean,
              national_quota,
              national_quota_mean = mean(national_quota),
              national_quota_diff = national_quota - national_quota_mean,
              list,
              list_mean = mean(list, na.rm = TRUE),
              list_diff = list - list_mean,
              gdppc,
              gdppc_mean = mean(gdppc, na.rm = TRUE),
              gdppc_diff = gdppc - gdppc_mean) %>% 
    ungroup() %>% 
    filter(., complete.cases(.))
  
  bf_enr <- bf(ecec_enr ~ 
                 me(pge_diff, pge_diff_se) +
                 me(pge_mean, pge_mean_se) +
                 women_rep_diff +
                 women_rep_mean +
                 fmi_diff +
                 fmi_mean +
                 national_quota_diff +
                 national_quota_mean +
                 gdppc_diff +
                 gdppc_mean +
                 ecec_enr_lag +
                 (1|c|country) + (1|t|year))

  m1_enr_b <- brm(formula = bf_enr,  
                  data = ecec_enr_data2,
                  backend = "cmdstanr",
                  control=list(adapt_delta = 0.99, 
                               max_treedepth = 14),
                  warmup = 500, 
                  iter = 1000, 
                  chains = 4, 
                  cores = 4,
                  seed = 324)
  
  m1_data <- m1_enr_b$data
  
  m1_data_2sd <- m1_data %>% 
    select(pge_diff,
           pge_mean,
           women_rep_diff,
           women_rep_mean,
           fmi_diff,
           fmi_mean,
           national_quota_diff,
           national_quota_mean,
           gdppc_diff,
           gdppc_mean,
           ecec_enr_lag) %>% 
    summarize(across(everything(), by2sd)) %>% 
    pivot_longer(everything()) %>% 
    mutate(`.variable` = case_when(name == "pge_mean" ~ 
                                     "bsp_mepge_meanpge_mean_se",
                                   name == "pge_diff" ~
                                     "bsp_mepge_diffpge_diff_se",
                                   TRUE ~ paste0("b_", name)),
           var_names = c("Macroegalitarianism, Difference",
                         "Macroegalitarianism, Mean",
                         "Descriptive Representation, Difference",
                         "Descriptive Representation, Mean",
                         "Feminist Movement Strength, Difference",
                         "Feminist Movement Strength, Mean",
                         "National Quota, Difference",
                         "National Quota, Mean",
                         "GDP per Capita, Difference",
                         "GDP per Capita, Mean",
                         "Lagged Enrollment"),
           sd2 = ifelse(str_detect(.variable, "list_|fmi_diff|_lag"),
                        1,
                        value))
  
  coef_data0_m1_enr <- m1_enr_b %>% 
    as_draws_df() %>% 
    tidybayes::gather_draws(`bs?p?_.*`, regex = TRUE) %>% 
    filter(!str_detect(`.variable`, "_Intercept")) %>% 
    left_join(m1_data_2sd, by = join_by(.variable))
  
  cy_summary_m1 <- m1_data %>%
    count(country) %>%
    pull(n) %>%
    summary()
  
  save(ecec_enr_data2, 
       file = file.path(policy_path,
                        "data",
                        "ecec_enr_data2.rda"))
  
  save(m1_data, m1_data_2sd, coef_data0_m1_enr, cy_summary_m1, 
       file = file.path(policy_path,
                        "data",
                        "enr_results.rda"))
} else {
  load(file = file.path(policy_path, "data", "ecec_enr_data2.rda"))
  load(file = file.path(policy_path, "data", "enr_results.rda"))
}
```

```{r m1enrplot, fig.cap="Predicting Enrollment in Early Childhood Education and Care, Ages 0-2, in OECD Countries", fig.height = 7, fig.width = 7.5}
#| label: fig-m1-enr

ordered <- c("Macroegalitarianism, Difference",
             "Macroegalitarianism, Mean", 
             "Descriptive Representation, Difference",
             "Descriptive Representation, Mean",
             "Feminist Movement Strength, Difference",
             "Feminist Movement Strength, Mean", 
             "National Quota, Difference",
             "National Quota, Mean",
             "GDP per Capita, Difference",
             "GDP per Capita, Mean",
             "Lagged Enrollment") %>% 
  rev()

coef_data_m1_enr <- coef_data0_m1_enr %>% 
  mutate(std_coef = round(.value * sd2, 1),
         term = factor(var_names, levels = ordered)) %>%
  ggdist::median_qi(std_coef, .width = c(.8, .9)) %>%
  mutate(ci = paste0(round(.lower, 1), " to ", round(.upper, 1))) %>%
  left_join(m1_data_2sd, ., by = join_by(.variable))

coef_data_m1_enr_total <- coef_data0_m1_enr %>% 
  group_by(.chain, .iteration, .draw) %>% 
  mutate(alpha = mean(ifelse(name=="ecec_enr_lag", .value, NA_real_),
                      na.rm = TRUE)) %>% 
  ungroup() %>% 
  filter(alpha < .97) %>% 
  group_by(.variable) %>% 
  mutate(std_coef0 = round(.value * sd2, 1),
         std_coef = round(std_coef0/(1 - alpha), 1),
         term = factor(var_names, levels = ordered)) %>%
  ggdist::median_qi(std_coef, .width = c(.8, .9)) %>%
  mutate(ci = paste0(round(.lower, 1), " to ", round(.upper, 1))) %>%
  left_join(m1_data_2sd, ., by = join_by(.variable))

coef_plot_m1 <- coef_data0_m1_enr %>% 
  mutate(std_coef = .value * sd2,
         term = factor(var_names, levels = ordered)) %>% 
  filter(!str_detect(var_names, "Lagged")) %>% 
  ggplot(aes(y = term, x = std_coef)) +
  ggdist::stat_halfeye(.width = .8,
                       fill = "grey60",
                       linewidth = 2) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  theme_light() +
  xlab("Standardized Coefficients") +
  ylab(NULL) 

lag_plot_m1 <- coef_data0_m1 %>% 
  mutate(std_coef = .value * sd2,
         term = factor(var_names, levels = ordered)) %>% 
  filter(str_detect(var_names, "Lagged")) %>% 
  mutate(term = "Lagged Enrollment") %>% 
  ggplot(aes(y = term, x = std_coef)) +
  ggdist::stat_halfeye(.width = .8,
                       fill = "grey60",
                       linewidth = 2) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  theme_light() +
  theme(strip.text.x = element_blank(),
        strip.background = element_blank()) +
  xlab("Unstandardized Coefficient") +
  ylab(NULL)

coef_plot_m1 + lag_plot_m1 +
  plot_layout(ncol = 1, widths = c(1, 1), heights = c(7, 1)) +
  plot_annotation(caption = "Notes: Dots indicate posterior medians; whiskers describe 80% credible\nintervals; shading depicts the posterior probability distribution.")
```

In this relatively small dataset, only a few of the posterior distributions of the coefficient estimates exhibit a bulk of their probability far from zero.
Countries with higher GDP per capita exhibit higher childcare enrollments among the very young, with a two-standard-deviation difference in the mean estimated to yield `r get_coef("gdppc_mean", coef_data_m1_enr)` points higher enrollments immediately and `r get_coef("gdppc_mean", coef_data_m1_enr_total)` points over time.
Countries with higher mean gender quotas also have higher enrollments, with a two-standard-deviation difference in mean national quota levels corresponding to `r get_coef("quota_mean", coef_data_m1_enr)` percentage points more of the under-two population in childcare.
The dynamics of the model---the fact that past enrollments strongly predict future enrollments---means this increase grows to `r get_coef("quota_mean", coef_data_m1_enr_total)` points over time.

Most important for our inquiry, when gender egalitarian attitudes increase among the public within a country, subsequent childcare enrollments rise as well.
The estimated year-to-year gain in enrollment following a two-standard-deviation rise in macroegalitarianism is `r get_coef("pge_diff", coef_data_m1_enr)` percentage points, and this gain compounds to `r get_coef("pge_diff", coef_data_m1_enr_total)` points dynamically.
Part of this estimate may well reflect that when egalitarian views grow in the public, more members of the public take advantage of the childcare that is available even in the absence of policy change; this is the precise reason why we sought to focus our inquiry on policy outputs like the WBL policy index rather than outcomes.
Still, legislators better representing the views of a more egalitarian public by pursuing policy changes that makes childcare more accessible are likely part of the story as well.

And how does the public respond?
@Sjoberg2004 argues that institutionalized family policies, particularly the provision of early childhood education and care, promote married women's labor force participation and so reshape the public's attitudes on gender egalitarianism in the public sphere.
That is, because these policies "contain normative elements and expectations on the 'proper' role of men as well as women in society and in the family" [@Sjoberg2004, 113], they can be expected to reinforce and increase macroegalitarianism.
But a thermostatic reaction, a backlash to increased gender equality in policies like those affecting childcare, also remains a possibility.


```{r enrsem_results.rda}    
if (!file.exists(file.path(policy_path, "data", "enrsem_results.rda"))) {  
  bf_pge <- bf(pge ~ 
                 ecec_enr_diff +
                 ecec_enr_mean +
                 women_rep_diff +
                 women_rep_mean +
                 fmi_diff +
                 fmi_mean +
                 national_quota_diff +
                 national_quota_mean +
                 gdppc_diff +
                 gdppc_mean +
                 pge_lag +
                 (1|c|country) + (1|t|year))

  m2_enrsem_b <- brm(formula = bf_enr + 
                      bf_pge + 
                      set_rescor(TRUE),  
                    data = ecec_enr_data2,
                    backend = "cmdstanr",
                    control=list(adapt_delta = 0.99, 
                                 max_treedepth = 14),
                    warmup = 500, 
                    iter = 1000, 
                    chains = 4, 
                    cores = 4,
                    seed = 324)
  
  m2_data <- m2_enrsem_b$data
  
  m2_data_2sd <- m2_data %>% 
    select(pge_diff,
           pge_mean,
           women_rep_diff,
           women_rep_mean,
           fmi_diff,
           fmi_mean,
           national_quota_diff,
           national_quota_mean,
           gdppc_diff,
           gdppc_mean,
           ecec_enr_lag) %>% 
    summarize(across(everything(), by2sd)) %>% 
    pivot_longer(everything()) %>% 
    mutate(`.variable` = case_when(name == "pge_mean" ~ 
                                     "bsp_ececenr_mepge_meanpge_mean_se",
                                   name == "pge_diff" ~
                                     "bsp_ececenr_mepge_diffpge_diff_se",
                                   TRUE ~ paste0("b_ececenr_", name)),
           var_names = c("Macroegalitarianism, Difference",
                         "Macroegalitarianism, Mean",
                         "Descriptive Representation, Difference",
                         "Descriptive Representation, Mean",
                         "Feminist Movement Index, Difference",
                         "Feminist Movement Index, Mean",
                         "National Quota, Difference",
                         "National Quota, Mean",
                         "GDP per Capita, Difference",
                         "GDP per Capita, Mean",
                         "Lagged Enrollment"
           ),
           sd2 = ifelse(str_detect(.variable, "list_|_lag"),
                        1,
                        value),
           dv = "Enrollment") %>% 
    bind_rows(m2_data %>% 
                select(ecec_enr_diff,
                       ecec_enr_mean,
                       women_rep_diff,
                       women_rep_mean,
                       fmi_diff,
                       fmi_mean,
                       national_quota_mean,
                       national_quota_diff,
                       gdppc_mean,
                       gdppc_diff,
                       pge_lag) %>% 
                summarize(across(everything(), by2sd)) %>% 
                pivot_longer(everything()) %>% 
                mutate(`.variable` = paste0("b_pge_", name),
                       var_names = c("Enrollment, Difference",
                                     "Enrollment, Mean",
                                     "Descriptive Representation, Difference",
                                     "Descriptive Representation, Mean",
                                     "Feminist Movement Index, Difference",
                                     "Feminist Movement Index, Mean",
                                     "National Quota, Difference",
                                     "National Quota, Mean",
                                     "GDP per Capita, Difference",
                                     "GDP per Capita, Mean",
                                     "Lagged Macroegalitarianism"
                       ),
                       sd2 = ifelse(str_detect(.variable, "list_|_lag"),
                                    1,
                                    value),
                       dv = "Macroegalitarianism")) %>% 
    mutate(dv = factor(dv, levels = c("Enrollment",
                                      "Macroegalitarianism")))
  
  coef_data0_enrsem <- m2_enrsem_b %>% 
    as_draws_df() %>% 
    tidybayes::gather_draws(`bs?p?_.*`, regex = TRUE) %>% 
    filter(!str_detect(`.variable`, "_Intercept")) %>% 
    left_join(m2_data_2sd, by = join_by(.variable))
  
  save(m2_data, m2_data_2sd, coef_data0_enrsem, 
       file = file.path(policy_path,
                        "data",
                        "enrsem_results.rda"))
} else {
  load(file = file.path(policy_path, "data", "enrsem_results.rda"))
}
```

```{r m2enrplot, fig.cap="Predicting Enrollment in Early Childhood Education and Care, Ages 0-2, in OECD Countries", fig.height = 9, fig.width = 7.5}
#| label: fig-m2-enr

ordered_enrsem <- c("Macroegalitarianism, Difference",
                    "Macroegalitarianism, Mean", 
                    "Enrollment, Difference",
                    "Enrollment, Mean",
                    "Descriptive Representation, Difference",
                    "Descriptive Representation, Mean",
                    "Feminist Movement Index, Difference",
                    "Feminist Movement Index, Mean",
                    "National Quota, Difference",
                    "National Quota, Mean",
                    "GDP per Capita, Difference",
                    "GDP per Capita, Mean",
                    "Lagged Enrollment",
                    "Lagged Macroegalitarianism") %>% 
  rev()

coef_data_enrsem <- coef_data0_enrsem %>% 
  mutate(std_coef = round(.value * sd2, 2),
         term = factor(var_names, levels = ordered_enrsem)) %>%
  ggdist::median_qi(std_coef, .width = c(.8, .9)) %>%
  mutate(ci = paste0(round(.lower, 1), " to ", round(.upper, 1))) %>%
  left_join(m2_data_2sd, ., by = join_by(.variable))

coef_data_enrsem_total <- coef_data0_enrsem %>%  
  group_by(.chain, .iteration, .draw) %>% 
  mutate(alpha_enr = mean(ifelse(name=="ecec_enr_lag", .value, NA_real_),
                         na.rm = TRUE),
         alpha_pge = mean(ifelse(name=="pge_lag", .value, NA_real_),
                          na.rm = TRUE)) %>% 
  ungroup() %>% 
  group_by(.variable) %>% 
  mutate(std_coef0 = round(.value * sd2, 1),
         std_coef = if_else(dv == "Enrollment",
                            round(std_coef0/(1 - alpha_enr), 1),
                            round(std_coef0/(1 - alpha_pge), 1)),
         term = factor(var_names, levels = ordered_enrsem)) %>%
  ggdist::median_qi(std_coef, .width = c(.8, .9)) %>%
  mutate(ci = paste0(round(.lower, 1), " to ", round(.upper, 1))) %>%
  right_join(m2_data_2sd, by = join_by(.variable))

coef_plots_enrsem <- coef_data0_enrsem %>% 
  mutate(std_coef = .value * sd2,
         term = factor(var_names, levels = ordered_enrsem)) %>% 
  filter(!str_detect(var_names, "Lagged")) %>% 
  ggplot(aes(y = term, x = std_coef)) +
  ggdist::stat_halfeye(.width = .8,
                       fill = "grey60",
                       linewidth = 2) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  facet_grid(~ dv) +
  coord_cartesian(xlim = c(-6, 6)) +
  theme_light() +
  theme(strip.text.x = element_text(size = 10, color = "black"),
        strip.background = element_rect(fill = "white", colour = "white")) +
  xlab("Standardized Coefficients") +
  ylab(NULL)

lag_plots_enrsem <- coef_data0_enrsem %>% 
  mutate(std_coef = .value * sd2,
         term = factor(var_names, levels = ordered_enrsem)) %>% 
  filter(str_detect(var_names, "Lagged")) %>% 
  mutate(term = "Lagged Response Variable") %>% 
  ggplot(aes(y = term, x = std_coef)) +
  ggdist::stat_halfeye(.width = .8,
                       fill = "grey60",
                       linewidth = 2) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  facet_grid(~ dv) +
  theme_light() +
  theme(strip.text.x = element_blank(),
        strip.background = element_blank()) +
  xlab("Unstandardized Coefficients") +
  ylab(NULL) 

coef_plots_enrsem + lag_plots_enrsem +
  plot_layout(ncol = 1, widths = c(1, 1), heights = c(9, 1)) +
  plot_annotation(caption = "Notes: Dots indicate posterior medians; whiskers describe 80% credible\nintervals; shading depicts the posterior probability distribution.")
```

@fig-m2-enr shows the results of a simultaneous-equations model of childcare enrollments and macroegalitarianism.
On the left of the plot, we see that the results of the model of enrollments presented in @fig-m1-enr remain substantively unchanged when the potential endogenous relationship between the two variables is included in the model.
On the right are the results predicting macroegalitarianism.
Looking at the estimates toward the top of that side reveals that countries with higher mean enrollments tend somewhat to have higher levels of macroegalitarianism.
A country with an enrollment rate a standard deviation above the overall mean, like those of Belgium or New Zealand, is estimated to have a PGE score `r get_coef("enr_mean", coef_data_enrsem)` points higher than an otherwise similar country with enrollments a standard deviation below the mean, similar to that of Hungary, compounding to `r get_coef("enr_mean", coef_data_enrsem_total)` over time.
The posterior distribution indicates that the probability that this estimate is positive, given this model and these data, is `r {{coef_data0_enrsem %>% filter(name == "ecec_enr_mean" & .value > 0) %>% nrow()}/20} %>% round()`%.
Changes in enrollment levels within a country over time, however, do not provide evidence for a short-term effect on macroegalitarianism.
It would seem that the private choices involved in enrolling one's child in daycare are too opaque to trigger a response in public opinion on a year-to-year basis.
In any event, there is no evidence whatsoever that growing enrollments of very young children provoke a thermostatic decline in macroegalitarianism. 

\pagebreak
## Conclusions

In this chapter, we examined policy representation of public opinion toward gender roles in the public sphere as well as the public's responsiveness to policies that advance gender equality.
We considered the most common policy focused on gender equality in politics, national legislative gender quotas, and a comprehensive measure of policies enabling gender equality in employment and entrepreneurship, the World Bank's Women, Business and the Law policy index.
As a further check on our conclusions, we also examined a policy outcome long understood to be crucial to gender equality in the workplace, enrollments in childcare for children under age two.

Our findings with regard to policy representation are unequivocal.
As the public adopts more gender egalitarian views, legislators are more likely to pass more demanding mandatory gender quotas, laws that require women to make up a specified share of parties' candidates for the legislature.
Such circumstances also make lawmakers more likely to adopt more of the policies that work to place women on equal footing to men in employment.
Even enrollments in childcare among the very young---a complex outcome reflecting policies influencing cost, accessibility, and quality of center-based care as well as the private decisions of parents---responds to shifts in macroegalitarianism.


