```{r setup, include=FALSE}
options(tinytex.verbose = TRUE)

knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  cache = TRUE,
  dpi = 600,
  fig.width = 7,
  fig.height = 4,
  plot = function(x, options)  {
    hook_plot_tex(x, options)
  }
)

if (!require(pacman)) install.packages("pacman")
library(pacman)
# load all the packages you will use below 
p_load(
  tidyverse,
  here,
  countrycode,
  patchwork,
  ggthemes,
  ggrepel,
  # ggmagnify,
  # ggdist,
  RColorBrewer
  # imputeTS,
  # osfr,
  # brms,
  # tabulizer,
  # tidybayes,
  # repmis,
  # rsdmx,
  # rvest,
  # vdemdata,
  # modelsummary,
  # kableExtra
) 

oecd_countries <- c("Australia", "Austria", "Belgium",
                    "Canada", "Chile", "Colombia",
                    "Costa Rica", "Czechia", "Denmark",
                    "Estonia", "Finland", "France", 
                    "Germany", "Greece", "Hungary",
                    "Iceland", "Ireland", "Israel",
                    "Italy", "Japan", "South Korea",
                    "Latvia", "Lithuania", "Luxembourg",
                    "Mexico", "Netherlands", "New Zealand",
                    "Norway", "Poland", "Portugal", 
                    "Slovakia", "Slovenia", "Spain",
                    "Sweden", "Switzerland", "Turkey", 
                    "United Kingdom", "United States")

wordify_numeral <- function(x) setNames(c("one", "two", "three", "four", "five", "six", "seven", "eight", "nine", "ten", "eleven", "twelve", "thirteen", "fourteen", "fifteen", "sixteen", " seventeen", "eighteen", "nineteen"), 1:19)[x]
```

# Introduction [Still Drafty]

Vignette of the 2022 Korean presidential election.  Conservative appeals to anti-egalitarian sentiment and pledge to abandon policies advancing equality.  Opponent initially does too but eventually abandons "lite" strategy, and argues for gender equality.  Many observers view the election as a referendum on gender equality.  Conservative wins, restricts the Women's Institute, and so on.  Did these results really represent the views on gender equality of the Korean public?

@Kim2022a

<!-- Both countries experienced transitions to democracy in the 1990s, and both enjoyed economic expansion that saw them rise to the ranks of the world's most advanced economies.  Both notoriously patriarchical. -->

Do parties and governments represent growing gender egalitarian public opinion by running higher numbers of successful women candidates and adopting policies that advance gender equality?
There is a lot of theory and empirical research on gender politics to suggest that they do.
Collective attitudes toward the appropriate roles of women and men in society---whether labeled culture, norms, ideology, or public opinion---constitute one of the primary explanations for the extent of women's inclusion in the traditionally masculine public sphere of the workforce, political power, and policy influence [see, e.g., @Paxton2021, 113-114].
Still, there are doubts.
Parties are well understood to be gatekeepers between aspiring candidates and political power [see, e.g., @Caul1999], and the party elites who control access to viable candidacies appear to frequently underestimate the public's desire to vote for women [see, e.g., @Norris1995].
And the multidimensionality of politics raises the possibility that even parties ostensibly favoring gender equality may nevertheless put measures promoting it behind other issues; the greater relative power of men to set the agenda within party organizations only makes this possibility more likely [see, e.g., @Htun2012, 553].

Public opinion research, too, is often skeptical of whether democratic representation occurs.
Some works contend that it happens only very slowly, on the scale of decades [see, e.g., @Caughey2022].
Political institutions including presidentialism, bicameral legislatures, and even, in some circumstances, coalition governments empower political minorities to block the enactment of policies favored by public opinion [see, e.g., Powell2000; Tsebelis2002].
There is considerable evidence, too, that it is the preferences of the rich, rather than those of the public as a whole, that influence policymakers [see, e.g., @Bartels2008 in the case of the United States; @Persson2024 across Europe].

But if we assume for the moment that Korean views on gender equality were represented in the results of Korea's 2022 "incel election," it raises the question of why the Korean public is so anti-egalitarian.
Some observers see events like these as signs of a recurring backlash in the public against women in the public sphere and policy efforts to promote gender equality.
The foundational book, _Backlash: The Undeclared War Against American Women_, argues that shifts in mass attitudes against gender equality in the United States "have always been triggered by the perception \ldots that women are making great strides" [@Faludi1991, xix].
@Shiran2024 describes how "moral panics" against women in politics spread after the adoption of gender quotas, the most effective policy for quickly shifting politics in a gender egalitarian direction.
Showing the opposite side of the coin, @Wlezien1993 documents how support for reproductive rights increased in the United States during the 1980s as successive court opinions and state laws made access to abortion more restrictive.

A prominent line of public opinion research, in fact, suggests that backlash may be a general phenomenon.
The influential theory of thermostatic public opinion contends that policy change triggers the public to revise attitudes in the opposite direction---that as the government provides more of anything, public demand for that thing will become sated and so preferences will shift against additional provision [@Wlezien1995].
Arguments for such "self-undermining" feedback, in which policies create opposition to their own continued provision [@Busemeyer2021, 144], are common across the study of public opinion on topics as diverse as budgetary policy [see, e.g., @Soroka2010], marriage equality and gay rights [for an overview, see @Bishin2021, 3-10], and public pension reform [see, e.g., @Weaver2010; @Fernandez2013].

But public opinion scholars have also found that many policies create their own constituencies, that is, after a policy is adopted, public opinion moves further in its support rather than swinging to oppose it. 
Drawing on the observation that "new policies create a new politics" [@Schattschneider1935, 288], an extensive literature in public opinion research proposes such "accelerating" feedback [@Busemeyer2021, 144].
For example, despite a lingering partisan cleavage, U.S. public opinion toward the Affordable Care Act grew steadily more favorable after its adoption [@Jacobs2018; @Brodie2020].
Arguments that public opinion toward gender equality in politics and employment reacts positively to the election of women and gender egalitarian policy adoption are common as well [see, e.g., @Barnes2016; @Lomazzi2019; @Kim2023].

All of this is to say that, despite substantial theorizing, these two questions---the extent of democratic representation of gender egalitarian public opinion and the nature of public responsiveness to developments toward gender equality in politics and policy---remain unsettled.
This is surprising given their importance.
Democracy itself depends on democratic representation, that a government's policies reflect "the preferences of its citizens, considered as political equals" [Dahl1973, 1].
If purportedly democratic countries diverge from these preferences in matters directly affecting the lives of half of their populations and scarcely a step away from those of the rest, that fact alone would cast deep doubt on the quality of their democratic institutions.
And if electoral results or policy change in favor of equality for women, the largest historically marginalized group in any country, regularly prompt a backlash in public opinion, how can feminist activists or indeed advocates for any disadvantaged group work to advance their cause over the long term [cf. @Bishin2021, 7]?

In the next section, we document that one reason these questions remain open is a severe lack of comparable and longitudinal data regarding public opinion on gender roles in the public sphere of politics and paid work.
Remedying this shortcoming of the extant surveys and the existing literature is perhaps the biggest advantage of the research presented in this book.
Doing so allows us to find that, happily for the state of democracy but---as in the case of Korea---not always so for women's rights, the governments of the world's rich democratic countries do represent public opinion with regard to gender equality.
Moreover, we find that public responsiveness on this matter follows a pattern of accelerating feedback, in which gains presage additional gains.

But before we go on, we should mention that widely-held attitudes toward gender roles have often been labeled as aspects of ideology or norms or culture.
To connect literatures, we will mainly refer to these attitudes, aggregated across the population of a country, as public opinion.
Specifically, we will call egalitarian public opinion toward gender roles in politics and the workplace as macroegalitarianism.

Another point of clarification is perhaps warranted.
The question of women's representation in all its dimensions is vitally important, and it is the topic of a large and vibrant body of research [see, among recent additions, @Betz2023; @Wang2023; @Klay2025].
It is not however the exact question we investigate here.
We start instead from the scholarship on public opinion and so rather ask about the representation and responsiveness of the public as a whole with regard to gender role attitudes.
These inquiries overlap, of course.
When women gain elected office is one point that falls into the shared area.
The former body of research has generated a great deal of scholarship on this topic, including some studies that directly address how gender egalitarian public opinion matters.
But these inquiries also diverge.
As a result, we avoid some issues that are central to the study of women's representation.
For example, defining and measuring what constitutes the substantive representation of women's interests is a serious and ongoing challenge for research [see, e.g., @Weeks2022a].
As @Young1997 [, 351] observes, "women are everywhere, and differ so vastly along so many dimensions that it seems absurd to suggest" that they agree on some set of interests that could be represented.
For our purposes, though, we need not assume that women's interests are served by, for instance, policies advancing gender equality in employment because no such assumption is needed to determine whether and how these policies reflect the entire public's views.
Still, both vantages are crucial to understanding democracy, and we hope readers coming from both perspectives will find that the answers we reach here speak to their concerns.


## A Scholarship Limited by the Available Data {#sec-scholarship}

Are the public's views on gender roles in the public sphere represented in what parties and policymakers do?
And how does the extent of gender egalitarianism in the public change in response?
Much of the reason these questions have yet to be fully answered is that data on the concept of macroegalitarianism is scant.
Even a half century after @RuleKrauss1974 [, 1719] called for more and better data on collective attitudes on gender roles, what we have available to us remains inadequate for fully examining their causes and consequences.
In the decades since that call, national and cross-national surveys have included a plethora of relevant questions, but sustained focus has been scant and the variety of these survey items renders the resulting data incomparable.
As a consequence, cross-national research has been constrained to study countries at just one or a few time points [see, e.g., @Paxton2003; @Alexander2012; @Glas2019a] or to rely on proxies such as predominant religion or the percentage of women in office [see, e.g., @Burns2001, 340-341; @Claveria2014; @Barnes2018].

```{r}
#| label: fig-proj-kt
#| fig-cap: "Countries and Mean Years Observed in Survey Datasets"
#| fig-height: 4.75
#| fig-width: 7.5
#| fig-pos: 'h'

dcpo_input_raw <- read_csv(here::here("paper",
                                      "measuring_egalitarianism",
                                      "data", 
                                      "dcpo_input_raw_pge.csv"),
                           col_types = "cdcddcd")

proj_kt <- dcpo_input_raw %>% 
  filter(r == 1) %>% 
  select(country, year, survey, item) %>% 
  mutate(proj = str_remove_all(survey, "\\d+") %>% 
           str_remove_all("_[^,]+") %>% 
           str_replace_all("\\b([^,]+), \\1", "\\1") %>% 
           str_replace_all("\\b([^,]+), \\1", "\\1")) %>% 
  separate(proj, into = paste0("proj", 1:5), fill = "right") %>% 
  pivot_longer(cols = starts_with("proj"), values_to = "project") %>% 
  filter(!is.na(project) & !project == "") %>% 
  select(country, year, project, item) %>% 
  distinct() %>% 
  group_by(project, item) %>% 
  mutate(cy = n_distinct(country, year)) %>% 
  group_by(project) %>% 
  arrange(-cy) %>% 
  filter(cy == max(cy)) %>% 
  summarize(cy = n_distinct(country, year),
            k = n_distinct(country),
            t = cy/k) %>% 
  group_by(k, t) %>% 
  mutate(to_jitter = n() > 1) %>% 
  ungroup() %>% 
  mutate(proj_name = toupper(project) %>% 
           str_replace("USGSS", "U.S. GSS") %>% 
           str_replace("USPEW", "Pew U.S. Politics") %>% 
           str_replace("PEWREL", "Pew Religion") %>% 
           str_replace("^PEW$", "Pew Global") %>% 
           str_replace("AMB", "AmB") %>% 
           str_replace("PGSS", "Polish GSS") %>% 
           str_replace("KOWEPS", "Korea Welfare Panel Study") %>% 
           str_replace("JGSS", "Japanese GSS") %>% 
           str_replace("SOM", "SOM (Sweden)") %>% 
           str_replace("ALLBUS", "ALLBUS (Germany)"))

proj_kt_plot <- ggplot(proj_kt, aes(y = t, x = k)) +
  geom_point(data = proj_kt %>% filter(!to_jitter),
             alpha = .3) +
  geom_point(data = proj_kt %>% filter(to_jitter),
             alpha = .3,
             position = position_jitter(width = .25, height = .25)) +
  ggrepel::geom_text_repel(data = subset(proj_kt, cy > 80 | t > 8 | k > 45),
                           aes(label = proj_name),
                           nudge_x = 5) +
  theme_bw() +
  scale_x_continuous(breaks=seq(0, 100, 25)) +
  labs(x = "Countries Observed",
       y = "Mean Years Observed Per Country Observed",
       title = "Survey Projects with Questions on\nGender Equality in Work and Politics")

proj_kt_plot + plot_annotation(caption = str_wrap("Notes: The number of countries and mean years observed are plotted only for the most frequently asked single question on attitudes toward women's equality in each survey project.", width = 114))
```

@fig-proj-kt illustrates the trade-off in available survey datasets including questions on attitudes toward gender roles between the breadth of country coverage and the number of years available for each country.
It plots, for each survey project, the number of countries for which data on gender egalitarian attitudes are available against the mean number of years these data are available per country.
Some survey projects ask more than one question on the topic, but here, only the most frequently asked single question on the topic is shown.
An 'L' shape is readily evident.
Many surveys, clustered in the lower left at the bend in the L, ask questions about support for gender equality in only a few different country-year contexts.
Some though, such as the U.S. General Social Survey (GSS) and the Swedish Society, Opinion, and Media (SOM) project in the top left, have fielded such questions repeatedly over many years in a single country, although even these efforts fall short of complete time series.
Others, including the World Values Survey (WVS) and the Pew International Religion Surveys along the bottom and towards the right, provide information about many countries across one or a few years.
The International Social Survey Program (ISSP), which surveyed respondents in 52 countries in as many as nine years (mean: 4.3 years) over two decades, provides the most over-time data for the most countries.
No single survey combines broad, cross-regional country coverage with longitudinal time-series data.

```{r}
#| label: fig-gr
#| fig-cap: "Countries and Mean Years Observed in Prominent Research"
#| fig-height: 6
#| fig-width: 7.5
#| fig-pos: 'h'


cited <- tribble(~citation, ~text_x, ~text_y,
                 "Alesina et al. 2013", 1, -1,
                 "Scarborough et al. 2021", 7, 0,
                 "Glas and Spierings 2019", 0, 1,
                 "Schober 2013", 5, 0, 
                 "Arpino et al. 2015", 5, 0)

gr <- read_csv(here("paper",
                    "introduction",
                    "data-raw",
                    "wos_gr.csv"),
               show_col_types = FALSE) %>% 
  janitor::clean_names() %>% 
  mutate(year = publication_year,
         hits = times_cited_all_databases,
         last_names = str_remove_all(authors, ", [A-Z]{1,3}") %>% 
           str_to_title() %>% 
           str_replace_all(";", ",") %>% 
           {ifelse(str_count(., ",") > 1,
                   str_replace(., ",.*", " et al."),
                   .)} %>% 
           str_replace(", ([A-Z][a-z]+)$", ", and \\1") %>% 
           str_replace("^([A-Z][a-z]+(?:-[A-Z][a-z]+)?), and ([A-Z][a-z]+)$", "\\1 and \\2"),
         citation = paste(last_names, year),
         cy = k*t) %>% 
  group_by(k, t) %>% 
  mutate(to_jitter = n() > 1) %>% 
  ungroup() %>% 
  left_join(cited, by = "citation") %>% 
  mutate(cited = ifelse(citation %in% cited$citation, citation, NA_character_))

gr_alpha <- .2
gr_seed <- 3240

gr_plot <- ggplot(gr, aes(x = k,
                          y = t)) + 
  geom_point(aes(size = hits),
             data = gr %>% filter(!to_jitter),
             alpha = gr_alpha) +
  geom_point(aes(size = hits),
             data = gr %>% filter(to_jitter),
             alpha = gr_alpha,
             position = position_jitter(width = .2,
                                        height = .25,
                                        seed = gr_seed)) +
  ggrepel::geom_text_repel(data = gr,
                           aes(label = cited),
                           # color = "grey20",
                           nudge_x = gr$text_x,
                           nudge_y = gr$text_y,
                           size = 3.3) +
  theme_bw() +
  theme(legend.justification = c(.99,.99), 
        legend.position = c(.98,.98),
        legend.box.background = element_rect(color = "grey",
                                             fill="white")) +
  guides(size = guide_legend(override.aes = list(alpha = .1))) +
  scale_size(name = "Citations") +
  labs(x = "Countries Observed",
       y = "Mean Years Observed Per Country Observed",
       title = "Prominent Articles on\nPublic Opinion on Gender Roles") +
  annotate(geom = "rect", 
           xmin = 0, xmax = 5, 
           ymin = 0, ymax = 5.3,
           color = "black", 
           fill = NA,
           linewidth = .25 ) +
  annotate(geom = "segment",
           x = 0, y = 5.3, xend = 33, yend = 19.1,
           linetype = "dashed",
           linewidth = .25) +
  annotate(geom = "segment",
           x = 5, y = 0, xend = 50, yend = 7.5,
           linetype = "dashed",
           linewidth = .25)

zoom_plot <- ggplot(gr, aes(x = k,
                            y = t)) + 
  geom_point(aes(size = hits),
             data = gr %>% filter(!to_jitter),
             alpha = gr_alpha) +
  geom_point(aes(size = hits),
             data = gr %>% filter(to_jitter),
             alpha = gr_alpha,
             position = position_jitter(width = .5, 
                                        height = .25,
                                        seed = gr_seed)) +
  theme_bw() +
  theme(legend.position = "none",
        plot.background = element_rect(colour = "black",
                                       fill = "white",
                                       linewidth =.5)) +
  coord_cartesian(xlim = c(0, 5), ylim = c(0, 5)) +
  labs(x = NULL,
       y = NULL)

gr_plot + 
  inset_element(zoom_plot, 33.75/80, 7.4/20, 48.75/80, 17.4/20) +
  plot_annotation(caption = str_wrap("Notes: Overlapping points are jittered slightly to enhance visibility.  Citation counts are as reported by the Web of Science on January 4, 2025.  See Appendix A for details on this sample of prominent articles.", width = 120))

```

Data availability has influenced scholarship on the topic, as can be seen in @fig-gr.
Using the Web of Science, we assembled a sample of prominent published articles on attitudes toward gender equality (see Appendix A for details).
These articles were published from `r summary(gr$year)[[1]]` to `r summary(gr$year)[[6]]` (median: `r summary(gr$year)[[3]]`) and were cited in the Web of Science from `r summary(gr$hits)[[1]]` to `r summary(gr$hits)[[6]]` times (median: `r summary(gr$hits)[[3]]`).
We then examined these articles to find the number of countries and years investigated in each.
The zoomed inset of the plot highlights that many of these articles might be described as using a case-study research design: just over a quarter of this sample considers only a single year in only a single country.

Among the works that investigate more contexts, the data employed tend to be longitudinal or cross-national, but very rarely both.
Arrayed vertically at the left of the figure, more than a quarter of this sample looks only at change over time, examining two or more years of data within just one country.
The recent work of @Scarborough2021 employs U.S. GSS data in 21 years from 1977 to 2018 to examine how gender and racial attitudes covaried over this period.
Of the studies not using the U.S. GSS, @Schober2013 takes advantage of panel data in 16 waves of the British Household Panel Survey to assess how gender egalitarian attitudes influence changes in time use after parenthood.

Spread horizontally along the bottom of the plot, over a third of the sample considers data from multiple countries in a sole cross-section.
Not surprisingly given its position in @fig-proj-kt, the WVS is the most frequently used source among articles in the lower right of @fig-gr.
The highest number of countries is examined in the much-cited work of @Alesina2013, which collapses data from three waves of the WVS for a total of 79 countries into one cross-section to examine whether traditions of plow-based agriculture have a negative influence on the extent of egalitarian gender attitudes.

The observation of four decades ago of @Stimson1985 [, 914] that "[w]e do comparative analyses across space, dynamic analyses over time, but almost never do we do dynamic comparison," made with regard to political science, also holds true among these discipline-spanning prominent works on attitudes toward gender equality.
Research considering data from two or more countries _and_ two or more years per country encompass just one-tenth of these articles.
@Arpino2015 uses changes in attitudes toward gender equality in the labor market---and the gap between men and women in these attitudes---to predict the total fertility rate in 27 European and North American countries drawing on data from three waves of the combined WVS and European Values Survey.
The resulting 81 observations is the largest number of country-years analyzed in any of these prominent works. 
Pooling data from WVS and Arab Barometer surveys, Glas and Spierings [-@Glas2019a; along with a companion piece, @Glas2020] examined the relationship between feminism and religiosity among Arab Muslims in 15 countries across 51 country-years, an average of 3.4 years observed per country; this represents the greatest over-time variation of any cross-national study in this sample.
None of the articles including five or more countries is able to examine public opinion in more than five years in any of the countries included in their analyses.

That these L-shaped distributions in the available datasets and the resulting analyses should limit the confidence any of us can feel in our conclusions should be readily evident.
The single-country studies that make up the vertical part of the L, even those over many years, by their nature leave questions regarding the generalizability of their findings to other parts of the world [see, e.g., @King2021, 210; @Pepinsky2019, 193].
The cross-national analyses on the horizontal, with just one or perhaps a few time points to leverage, on the other hand, often raise concerns that differences across countries are being conflated with over-time causal processes [see, e.g., @Jackman1985, 173-174].

```{r, eval=FALSE}
#| label: fig-countries0
#| fig-cap: "Count of Prominent Articles Including Countries in Each Region"
#| fig-height: 6
#| fig-width: 7.5
#| fig-pos: 'h'

countries_by_cases <- read_csv(here("paper",
                                    "introduction",
                                    "data-raw",
                                    "countries.csv"),
                               show_col_types = FALSE) %>% 
  group_by(article) %>% 
  mutate(country = countrycode(country,
                               origin = "country.name",
                               destination = "country.name"),
         k = n(),
         cases = if_else(k>1, "cross_national",
                         "single_case")) %>% 
  ungroup() %>% 
  count(country, cases) %>% 
  group_by(country) %>% 
  mutate(total = sum(n)) %>% 
  ungroup() %>% 
  arrange(total, rev(country)) %>% 
  mutate(oecd = if_else(country %in% oecd_countries,
                        "OECD Countries",
                        "Non-OECD Countries"),
         country = as_factor(country),
         region = countrycode(country,
                              origin = "country.name",
                              destination = "region23"),
         oecd = as_factor(oecd))

countries <- read_csv(here("paper",
                           "introduction",
                           "data-raw",
                           "countries.csv"),
                      show_col_types = FALSE) %>% 
  mutate(country = countrycode(country,
                               origin = "country.name",
                               destination = "country.name")) %>% 
  count(country) %>% 
  arrange(n, rev(country)) %>% 
  mutate(oecd = country %in% oecd_countries,
         region = countrycode(country,
                              origin = "country.name",
                              destination = "region23"),
         region = case_when(country %in% 
                              c("Canada", "United States") ~
                              "North America",
                            str_detect(region, "Eastern Asia") ~ "East Asia",
                            str_detect(region, "Southern Asia") ~ "South Asia",
                            str_detect(region, "Western Asia") ~ "West Asia",
                            str_detect(country, "Taiwan") ~ "East Asia",
                            str_detect(country, "Russia") ~ "Central Asia",
                            str_detect(region, "Europe") ~ "Europe",
                            str_detect(region, "Caribbean|Central America|South America") ~ "Latin America & Caribbean",
                            str_detect(region, "Australia") ~ "Oceania",
                            str_detect(region, "Africa") ~ "Africa",
                            TRUE ~ region) %>% 
           fct_relevel("Africa",
                       "Central Asia",
                       "South Asia",
                       "Latin America & Caribbean",
                       "West Asia",
                       "East Asia",
                       "Europe",
                       "Oceania",
                       "North America"),
         iso2c = if_else(oecd,
                         countrycode(country,
                             origin = "country.name",
                             destination = "iso2c"),
                         NA_character_),
         jitter_height = if_else(region == "Europe",
                                 .25,
                                 0.01))

oecd_regions <- countries %>% 
  group_by(region, oecd) %>% 
  mutate(n_mean = if_else(oecd,
                          mean(n),
                          NA_real_),
         n_mean1 = replace_na(n_mean, mean(n)),
         iso2c = if_else(oecd,
                         countrycode(country,
                             origin = "country.name",
                             destination = "iso2c"),
                         NA_character_)) %>% 
  ungroup() %>% 
  arrange(-n_mean1) %>% 
  mutate(region = fct_relevel(region, 
                              "Northern America",
                              "Oceania",
                              ""))

# country_coverage_plot <- ggplot(data = countries %>% 
#                                   filter(oecd),
#                                 aes(y = country, x = n)) +
#   geom_bar(stat = "identity") +
#   theme_bw() +
#   labs(y = NULL,
#        x = "Articles")
# 
# region_coverage_plot <- ggplot(data = oecd_regions,
#                                 aes(y = region, x = n)) +
#   geom_boxplot() +
#   ylab(NULL) +
#   xlab("Articles")

# countries %>% 
#   ggplot(aes(x = n,
#              y = region)) +
#   geom_point(data = countries %>% 
#                   filter(!oecd),
#              alpha = .2,
#              position = position_jitter(height = .3,
#                                         seed = 10)) +
#   geom_text(data = countries %>% 
#                   filter(oecd & !(region %in% c("Europe",
#                                               "Latin America & Caribbean"))),
#             aes(label = iso2c),
#             size = 2.1) +
#   geom_text(data = countries %>% 
#               filter(oecd & (region %in% c("Europe",
#                                               "Latin America & Caribbean"))),
#             aes(label = iso2c),
#             size = 2.1,
#             position = position_jitter(width = .1,
#                                         height = .3,
#                                         seed = 10)) +
#   # scale_alpha_manual(values = c(.15, 1)) +
#   theme_bw() +
#   theme(legend.position="none") +
#   labs(y = NULL,
#        x = "Articles")

countries %>% 
  ggplot(aes(x = n,
             y = region)) +
  geom_point(data = countries %>% 
                  filter(!oecd),
             alpha = .2,
             position = position_jitter(height = .2,
                                        seed = 10)) +
  geom_text(data = countries %>% 
                  filter(oecd & !(region %in% c("Europe",
                                              "Latin America & Caribbean"))),
            aes(label = iso2c),
            size = 2.1) +
  geom_text_repel(data = countries %>% 
              filter(oecd & (region %in% c("Europe",
                                              "Latin America & Caribbean"))),
            aes(label = iso2c),
            size = 2.1,
            max.overlaps = 20) +
  theme_bw() +
  theme(legend.position="none") +
  labs(y = NULL,
       x = "Articles")
```

```{r}
#| label: fig-countries
#| fig-cap: "Count of Prominent Articles Including Each Country by Region"
#| fig-height: 6
#| fig-width: 7.5
#| fig-pos: 'h'

countries <- read_csv(here("paper",
                           "introduction",
                           "data-raw",
                           "countries.csv"),
                      show_col_types = FALSE) %>% 
  mutate(country = countrycode(country,
                               origin = "country.name",
                               destination = "country.name")) %>% 
  count(country) %>% 
  arrange(n, rev(country)) %>% 
  mutate(oecd = country %in% oecd_countries,
         region = countrycode(country,
                              origin = "country.name",
                              destination = "region23"),
         region = case_when(country %in% 
                              c("Canada", "United States") ~
                              "North America",
                            str_detect(region, "Eastern Asia") ~ "East Asia",
                            str_detect(region, "Southern Asia") ~ "South Asia",
                            str_detect(region, "Western Asia") ~ "West Asia",
                            str_detect(country, "Taiwan") ~ "East Asia",
                            str_detect(country, "Russia") ~ "Central Asia",
                            str_detect(region, "Europe") ~ "Europe",
                            str_detect(region, "Caribbean|Central America|South America") ~ "Latin America &\nCaribbean",
                            str_detect(region, "Australia") ~ "Oceania",
                            str_detect(region, "Africa") ~ "Africa",
                            TRUE ~ region) %>% 
           fct_relevel("Africa",
                       "Central Asia",
                       "South Asia",
                       "Latin America &\nCaribbean",
                       "West Asia",
                       "East Asia",
                       "Europe",
                       "Oceania",
                       "North America"),
         iso2c = countrycode(country,
                             origin = "country.name",
                             destination = "iso2c"),
         # iso2c = if_else(oecd,
         #                 countrycode(country,
         #                             origin = "country.name",
         #                             destination = "iso2c"),
         #                 NA_character_),
         jitter_height = if_else(region == "Europe",
                                 .25,
                                 0.01))

plot_seed <- 14; countries %>%
  ggplot(aes(x = n,
             y = region)) +
  geom_text(data = countries %>%
               filter(!oecd),
             aes(label = iso2c),
             size = 2.2,
             alpha = .3,
             position = position_jitter(height = .25,
                                        seed = plot_seed)) +
  # geom_point(data = countries %>%
  #                 filter(!oecd),
  #            alpha = .2,
  #            position = position_jitter(height = .25,
  #                                       seed = plot_seed)) +
  geom_text(data = countries %>%
                  filter(oecd & !(region %in% c("Europe",
                                              "Latin America &\nCaribbean"))),
            aes(label = iso2c),
            size = 2.2) +
  geom_text(data = countries %>%
              filter(oecd & (region %in% c("Europe",
                                              "Latin America &\nCaribbean"))),
            aes(label = iso2c),
            size = 2.2,
            position = position_jitter(width = .1,
                                        height = .33,
                                        seed = plot_seed)) +
  theme_bw() +
  theme(legend.position="none",
        axis.text.y = element_text(size=10)) +
  labs(y = NULL,
       x = "Articles",
       title = "Geographic Concentration in Prominent Articles on\nPublic Opinion on Gender Roles") +
  plot_annotation(caption = str_wrap("Notes: Countries are represented by their ISO-2 codes; OECD members are emphasized.  Overlapping observations are jittered slightly to enhance visibility.  See Appendix A for details on this sample of prominent articles.", width = 120))
```

This unease is compounded by the fact that this research is geographically concentrated.
While @fig-gr depicted the number of countries and years in each study in our sample of prominent works, @fig-countries takes the opposite perspective and shows the number of these articles that include each country.
One hundred eighteen countries are included in the analysis of at least one of the papers.
Eight countries are covered exactly once.
Considering the countries that are included in any of these works, the median is included just five times.
Not surprisingly, the advanced democracies of the Organization for Economic Cooperation and Development (OECD) are generally better studied in these prominent articles [cf. @Wilson2022, 1025].
All but two of a list of the top twenty most-included countries in this sample of prominent works are OECD members, and those non-OECD countries are ranked last (China, tied with four OECD members) and next to last (Brazil) on this list.
The median OECD country appears in `r countries %>% filter(oecd) %>% pull(n) %>% median() %>% wordify_numeral()` articles.
Still, there is considerable bias in coverage even among the OECD countries.
At one end, Costa Rica, Luxembourg, and Israel appear in just two, three, and four articles respectively.
At the other end, the United States is included in `r countries %>% filter(country == "United States") %>% pull(n)` works, nearly five times the OECD median and more than twice as many as the next most studied countries, Germany and the United Kingdom.
Indeed, among these works, the United States has been the subject of more _single-country_ studies---over one-fourth of our sample---than the number of articles even including any other single country.
It is a truism that the cases examined influence the conclusions reached [e.g., @Geddes1990], and as @Wilson2022 [, 1037] points out, geographic bias of the sort found in this literature makes the scope conditions of even cross-national studies difficult to discern.
In sum, a lack of data enabling researchers to look at developments over long stretches of time across many countries has prevented much research on how public opinion, politics, and policy interact with regard to questions of gender equality, and what scholarship exists is further undermined by pervasive geographic bias. 
That it addresses the absence of cross-national time-series data on attitudes toward gender equality is the first of the advantages of this book.

```{r eval=FALSE, include=FALSE}
# @Inglehart2003:
# "[T]raditional cultural attitudes have long been thought to present major barriers to women's representation in elected office, but previous studies have not present conclusive empirical evidence supporting this proposition.
# Theories of socialization have long emphasized the importance of the division of sex roles within a country - especially egalitarian attitudes towards women as political leaders (Sapiro 1983; Carroll 1994). Cultural explanations hypothesize that in traditional societies, women will be reluctant to run and, if they seek the office, will fail to attract sufficient support to win.
# Cultural attitudes may have a direct influence on whether women are prepared come forward as candidates for office (the supply-side of the equation), and the criteria used by gate-keepers when evaluating suitable candidates (the demand-side), as well as having an indirect influence upon the overall institutional context, such as the adoption of gender quotas in party recruitment processes (Lovenduski and Norris 1993; Norris 1997)."
# 
# @Woo2023:
# "The PGE dataset will allow researchers to not only better address such long-standing questions as how collective attitudes on gender roles have influenced the election of women to national legislatures and vice versa [see, e.g., @Paxton2003; @Alexander2012] but also, for example, to pursue both new and more nuanced lines of inquiry on issues of policy responsiveness and policy feedback [cf., @Kittilson2008; @Busemeyer2021]."
# 
# The extent of public support for gender egalitarianism has been an important issue in many countries around the world since at least the past half-century.
# The improvement of public gender egalitarianism over the globe makes scholars examine the causes and consequences of the improvement.
# A wide range of studies pay their attention on the determinants of public gender egalitarianism.
# For instance, according to the crucial study done by @Norris2001 which is consistent with the work from @Reynolds1999, the role of cultural rigidity, religion, and generational value is critical for the persistency and spread of gender egalitarianism.
# Some studies focus on the impacts of regime types such as democracy and autocracy as a focal determinant of gender equality @Beer2009, while other studies maintain that political elites play a key role in shaping public attitudes toward gender equality @Bulut2023.
# 
# How do societal attitudes toward gender roles influence women's political success and policy influence?
# Taking advantage of a comprehensive collection of survey data and recent advances in latent variable modeling of public opinion, this book provides new evidence of how and when public gender egalitarianism is translated into gender equality in countries around the world.
# 
# The influence of public support for gender equality on various social and political phenomena has received wide attention from scholars (Cannavale et al., 2022; Cavero-Rubio et al., 2019; Concha, 2023; Kanas & Steinmetz, 2021; Kaufman et al., 2023; McThomas & Tesler, 2016; Mustafa & Almazrouei, 2020).
# For instance, @Winter2008 showed that U.S. voters' support for Hilary Clinton depended on their attitudes toward the women's movement and gender equality.
# More recently, @Bergqvist2013 examines both successful and unsuccessful cases and emphasizes the close association between public gender egalitarianism and gender equality policy adoption.
# 
# Despite the above-mentioned previous literature on the importance of public support for gender equality, the lack of time-series cross-national data on public opinion prevents us from fully understand its influence [@RuleKrauss1974].
# Especially, the causal influence of public gender egalitarianism on policy outcomes is still under a veil due to the lack of such data.
# Previous studies on the impact of public support for gender egalitarianism have largely relied on cross-sectional data with little or no leverage on change over time (Glas & Alexander, 2020; McThomas & Tesler, 2016; Paxton & Kunovich, 2003; Steel & Kabashima, 2008).
# Given the non-negligible changes in the public support for gender equality over decades (Bolzendahl & Myers, 2004; Eriksson‐Zetterquist & Renemark, 2016; Thijs et al., 2019), this is an unfortunate shortcoming that undermines our confidence in our current state of understanding.
# This book seeks to remedy this problem through the new Public Gender Egalitarianism (PGE) dataset, which provides a comparable time-series cross-national index for 124 countries over the years from 1972 to 2022, as well as other novel data.
```

## Advantages of This Research

```{r pge_stats}
load(here("data", "pge_summary.rda"))
n_countries <- pge_summary$country %>%
  unique() %>%
  length()

mean_years <- pge_summary %>%
  group_by(country) %>%
  summarize(years = max(year) - min(year) + 1) %>% 
  pull(years) %>% 
  mean() %>% 
  round(1)

```

The research presented in this book has several advantages over the existing scholarship on public opinion toward gender roles in the public sphere.
As just mentioned, the first involves data.
Drawing on recent advances in latent variable modeling of public opinion and a comprehensive collection of survey data, we update and expand the Public Gender Egalitarianism (PGE) dataset [@Woo2023] to address the need for comparable estimates of macroegalitarianism across countries and over time.
The resulting data include information on `r n_countries` countries, with a mean number of consecutive years per country of `r mean_years`.
In terms of @fig-proj-kt, the revised PGE dataset lands beyond the right hand border and toward the top, with more countries than any of the surveys and a greater mean number of years per country than all but two single-country surveys: Sweden's SOM and the U.S. GSS.
Moreover, the careful attention to the cross-national comparability of the PGE data reassures that a principal weakness of large-_n_ research is mitigated: weak internal validity due to the difficulties of measurement across countries [see @Jackman1985, 161; @Pepinsky2019, 193-194].
These new data on macroegalitarianism, based on thousands of surveys conducted in countries around the world, provides a description of macroegalitarianism's levels across countries and regions and its trends over time that is far more comprehensive than any previously available.
In turn, this comprehensive dataset allows us to examine the causes and consequences of macroegalitarianism---for present purposes, public responsiveness and democratic representation---together in comparative and dynamic perspective.

That our perspective is _broadly comparative_ is crucial.
These new data allows us to take a cross-national, cross-regional comparative approach and examine the experiences of all of the countries around the world to which the theories of representation and responsiveness mentioned above clearly apply.
Single-country studies have long been the dominant research design in comparative politics [see, e.g., @Munck2007, 22; @Schedler2010, 421; @Pepinsky2019, 192], as in the interdisciplinary sample of prominent works on attitudes toward gender roles we presented above, but such works often struggle to address concerns regarding external validity, that is, whether the findings reached in the country studied generalize to anywhere else [see, e.g., @Jackman1985, 164; @Lieberman2005, 441; @Findley2021, 381].
The same question is raised by even cross-national comparative studies that are regionally concentrated: there is not necessarily reason to suppose that their conclusions hold elsewhere.
By allowing us to look at advanced democracies in North America, Oceania, Europe, east Asia, west Asia, and Latin America, the PGE data increases the likelihood that our conclusions regarding macroegalitarianism will not be limited to the context of a single country or region.

The _dynamic_ perspective of our analyses is no less important.
It has long been understood that cross-sectional associations, that is, those established by looking only across countries at a single time, have several weaknesses that are not ameliorated no matter how broadly comparative the sample may be.
If we see that countries where the public holds more gender egalitarian views consistently also have adopted policies that advance gender equality, we still do not know whether the policy adoptions represent public opinion, or public opinion responds to policy change, or both, or neither---policy and public opinion may both result some other, unobserved cause [see, e.g., @Rustow1968, 48].
Because democratic representation and public responsiveness are necessarily processes that unfold over time, our evidence for these processes should look over time as well [e.g., @Stimson1995, 543; @Soroka2010, 22-23].
Pooling data across countries and over time in analyses that are both comparative _and_ dynamic has been long recognized as "an extraordinarily robust research design" for drawing causal inferences [@Stimson1985, 916; see also @Western1998; @Shor2007; @Bell2015; @Bell2019], and given the inability to experimentally manipulate any of our variables of interest---public opinion, women in office, or policy---it provides the best possible evidence of causation.

Moreover, a dynamic perspective examining change over time allows us to consider democratic representation _together with_ public responsiveness.
For representation to occur, changes in public opinion must be reflected in who is elected and the policies adopted; as macroegalitarianism increases, more gender equality should result.
The public's responsiveness involves an arrow running the opposite direction: changes in officeholding and policy influence the attitudes toward gender equality.
Previous works tend to look at either one side of this loop or the other.
The hazard of such a one-sided approach is the risk of simultaneity bias due to endogeneity.
This is a more subtle version of the direction-of-causality problem with cross-sectional work identified by @Rustow1968 [, 48].
If macroegalitarianism rises as a result of a gender egalitarian policy, then considering only whether public opinion causes policy can result in mistaking the former process for the latter.
Thanks to the long time series the PGE data make available to us to examine, we are able to disentangle these effects with confidence.

We further bolster confidence in our conclusions with attention to another source of bias.
@Findley2021 [, 368] notes that even---and indeed especially---research designs drawing on representative pooled time series may yet fail to yield generalizable findings as a result of variable selection bias, that is, differences between the way variables are operationalized in an analysis and the theoretical concepts of interest.
The PGE dataset, our operationalization of the concept of macroegalitarianism, incorporates the broad range of survey items that have been employed to measure public opinion toward gender roles in politics and the workplace, and we pay careful attention to its measurement validation.
And with regard to advancements toward gender equality---which constitute the outcome when assessing the extent of democratic representation and the treatment from the standpoint of theories of public responsiveness---we employ multiple indicators of gender equality in the traditionally masculine public sphere of politics and paid employment.
**@Beer2009 [, 217]: "there is some scholarly consensus that gender equality should be assessed in terms of three domains: capabilities, opportunities, and empowerment/agency" @Bericat2012: "education, work and power"**
We examine (a) women's descriptive representation in national legislatures, the most commonly used measure of gender equality in politics; (b) the adoption and reform of gender quotas, the policy most closely linked to advancing gender equality in politics; (c) the World Bank’s Women, Business, and Law v1.0 policy index [@WorldBank2024], a count of thirty-five policies that advance gender equality in the workplace; and (d) childcare enrollments, a policy outcome closely linked to gender equality in paid employment.^[
The policies we consider, then, are among those @Htun2010 [, 210, 209] calls _non-doctrinal_: they do not "touch upon the jurisdictional conflict between the state and other organizations over the administration of kinship relations, reproduction, and sexuality" and so do not "challenge religious doctrine or the codified tradition of a major cultural group."
One benefit of this aspect of the policies we examine is that our analyses do not require a cross-nationally comparable measure of the strength of religious institutions as opponents to reform.]
The near uniformity of our findings across this diversity of measures provides reassurance that variable selection bias does not undercut the generalizability of our conclusions.

Finally, we complement our expansive cross-national over-time analyses with an in-depth case study.  **Talk about case studies. Multilevel research design @Lieberman2005; generalizability across units @Findley2021; subnational research design @Snyder2001**


## Plan of the Book

The book proceeds as follows.
In the next chapter, we review the theories and existing evidence on the relationships among gender egalitarian public opinion, women's descriptive representation, and public policies advancing gender equality.

In Chapter 3, we develop our cross-national and longitudinal measure for our concept of macroegalitarianism.
After describing how this measure, the Public Gender Egalitarianism scores, is estimated, we use them to show how macroegalitarianism varies across countries and how these attitudes have changed over the past three decades around the world.

Chapter 4 narrows our geographic focus to the countries where theories of representation and responsiveness are most applicable, the advanced democracies that constitute the OECD.
There, we explore the implications of these theories for women's descriptive representation, and in particular, women's success in winning election to national legislatures.
Our analyses show that increases in macroegalitarianism predict subsequent gains in descriptive representation for women and that, in turn, the public responds to more women in office not with a backlash but instead by growing even more egalitarian in their views.

Chapter 5 turns to the adoption of policies advancing gender equality in the public sphere, both in politics and in paid employment.
Looking again across the OECD, it finds that governments represent the views of their citizens: when macroegalitarianism increases, laws setting national legislative gender quotas and policies that put women on equal footing in the workforce are more likely to be adopted.
Intriguingly, these effects do not appear to work through improvements in descriptive representation: when the public becomes more egalitarian, it seems that both men and women legislators represent their constituents by favoring policies that advance gender equality.
We find some evidence of public responsiveness in this chapter as well.
All of this evidence indicates that policymaking and public opinion constitute a virtuous circle, that the adoption of policies advancing gender equality leads, if anything, to more macroegalitarianism rather than to the backlash of a thermostatic response.

In Chapters 6 and 7, we further examine the relationships between public opinion, descriptive representation, and policy outcomes in case studies of Mexico and South Korea, delving into the processes by which gender egalitarian attitudes are, and are not, converted into political outcomes that further gender equality.
As we suggested in the opening pages, Mexico is a case that has seen rapid and dramatic changes in attitudes and policy in recent decades while Korea, on the other hand, has not witnessed such developments.
Our findings from these two cases shed additional light on the reciprocal relationships between macroegalitarianism, women's descriptive representation, and the adoption of policies advancing gender equality.

Chapter 8 concludes the book by reviewing the evidence for dynamic democratic representation and public responsiveness.
It considers the implications of our findings of dynamic democracy for political science's understanding of public opinion and of the politics of gender, as well as their implications for policy and for democracy.
