# Appendices

\setcounter{figure}{0}
\renewcommand{\thefigure}{A\arabic{figure}}
\setcounter{table}{0}
\renewcommand{\thetable}{A\arabic{table}}

```{r setup, include=FALSE}
options(tinytex.verbose = TRUE)

knitr::opts_chunk$set(cache = FALSE, echo = FALSE, message = FALSE, warning = FALSE)

# If `DCPOtools` is not yet installed:
# remotes::install_github("fsolt/DCPOtools")

# If development version of `DCPO` is not yet installed:
# remotes::install_github("fsolt/DCPO")

library(DCPOtools)
library(DCPO)
library(tidyverse)
library(glue)
library(countrycode)
library(patchwork)
library(modelsummary)
library(here)

set.seed(324)

oecd_countries <- c("Australia", "Austria", "Belgium",
                    "Canada", "Chile", "Colombia",
                    "Costa Rica", "Czechia", "Denmark",
                    "Estonia", "Finland", "France", 
                    "Germany", "Greece", "Hungary",
                    "Iceland", "Ireland", "Israel",
                    "Italy", "Japan", "South Korea",
                    "Latvia", "Lithuania", "Luxembourg",
                    "Mexico", "Netherlands", "New Zealand",
                    "Norway", "Poland", "Portugal", 
                    "Slovakia", "Slovenia", "Spain",
                    "Sweden", "Switzerland", "Turkey", 
                    "United Kingdom", "United States")
```

\pagebreak
## Appendix A: Sample of Published Articles on Public Opinion Toward Gender Equality

To generate a sample of published articles on gender egalitarianism, we searched the Web of Science.
Web of Science topic searches return articles in which the search terms appear in the title or abstract.
We executed the following search: `TS = (("public opinion" OR attitudes OR culture) AND ((women* OR gender) AND (equal* OR egalitarian*)))`.
After filtering false positives---articles that do not include a measure of public attitudes toward gender equality or gender roles---the eighty most cited empirical research articles returned compose our sample.
Each of the articles was then consulted to identify its number of countries and mean years observed per country.
This information is listed in Table A1 below.

\pagebreak
\noindent Table A1: Prominent Research Articles on Public Opinion Toward Gender Roles
```{r articles_table}
gr <- read_csv(here("paper",
                    "introduction",
                    "data-raw",
                    "wos_gr.csv"),
               show_col_types = FALSE) %>% 
  janitor::clean_names() %>% 
  mutate(year = publication_year,
         hits = times_cited_all_databases,
         last_names = str_remove_all(authors, ", [A-Z]{1,3}") %>% 
           str_to_title() %>% 
           str_replace_all(";", ",") %>% 
           {ifelse(str_count(., ",") > 1,
                   str_replace(., ",.*", " et al."),
                   .)} %>% 
           str_replace(", ([A-Z][a-z]+)$", ", and \\1") %>% 
           str_replace("^([A-Z][a-z]+(?:-[A-Z][a-z]+)?), and ([A-Z][a-z]+)$", "\\1 and \\2"),
         citation = paste(last_names, year) %>% 
           ifelse(. == "Andersen and Fetner 2008" &
                    !str_detect(source_title, "AMERICAN"),
                  "Andersen and Fetner 2008a",
                  .) %>% 
           ifelse(. == "Lax and Phillips 2009" &
                    !str_detect(source_title, "JOURNAL"),
                  "Lax and Phillips 2009a",
                  .) %>% 
           ifelse(. == "Brewer 2003" &
                    !str_detect(source_title, "OPINION"),
                  "Brewer 2003a",
                  .),
         cy = k*t)

gr %>% 
  arrange(-hits) %>% 
  transmute(Article = citation,
            `Countries Observed` = as.character(k),
            `Mean Years Observed per Country` = as.character(round(t, 1)),
            `Country-Years Observed` = as.character(round(cy)) %>%
              str_trim(),
            `WoS Citations` = as.character(hits)) %>% 
  modelsummary::datasummary_df(output = "kableExtra",
                               longtable = TRUE) %>%
  kableExtra::column_spec(1, width = "14em") %>%
  kableExtra::column_spec(c(2, 3, 4, 5), width = "6em") %>%
  kableExtra::kable_styling(font_size = 10) %>%
  kableExtra::kable_styling(latex_options = c("repeat_header")) # %>%
  # kableExtra::kable_styling(latex_options = "striped")
```


\pagebreak

## Appendix A: Survey Items Used to Estimate Public Gender Egalitarianism
```{r item_summary, cache = FALSE, cache.extra = tools::md5sum(here::here("data-raw", "dcpo_input_raw_public.csv"))}
surveys_pge <- read_csv(here("paper",
                             "measuring_egalitarianism",
                             "data-raw",
                             "surveys_pge.csv"),
                        col_types = "cccccnn")

dcpo_input_raw_pge <- read_csv(here("paper",
                                    "measuring_egalitarianism",
                                    "data",
                                    "dcpo_input_raw_pge.csv"),
                               col_types = "cdcddcd")

load(here::here("data", "item_results.rda"))

process_dcpo_input_raw <- function(dcpo_input_raw_df) {
  dcpo_input_raw_df %>% 
    with_min_yrs(2) %>% 
    with_min_cy(5) %>% 
    filter(year >= 1972) %>% 
    group_by(country) %>% 
    mutate(cc_rank = n()) %>% 
    ungroup() %>% 
    arrange(-cc_rank)
} 

dcpo_input_raw_pge1 <- process_dcpo_input_raw(dcpo_input_raw_pge)

items_summary <- dcpo_input_raw_pge1 %>%
  dplyr::select(country, year, item, survey) %>%
  separate_rows(survey, sep=",\\s+") %>% 
  distinct() %>%
  group_by(item) %>% 
  mutate(survey = str_extract(survey, "^[a-z]*"),
         all_surveys = paste0(unique(survey), collapse = ", ")) %>% 
  ungroup() %>% 
  distinct(country, year, item, .keep_all = TRUE) %>% 
  group_by(item) %>% 
  mutate(n_cy = n()) %>% 
  ungroup() %>%
  distinct(item, n_cy, all_surveys) %>% 
  left_join(surveys_pge %>%
              select(item, question_text) %>%
              distinct(item, .keep_all = TRUE),
            by = "item") %>% 
  left_join(alpha_results, by = "item") %>% 
  left_join(beta_results, by = "item") %>% 
  arrange(-n_cy)

```

```{r dcpo_items_table}
#| label: tbl-items

items_summary %>% 
  transmute(`Survey\nItem\nCode` = item,
            `Country-Years` = as.character(n_cy),
            `Question Text` = str_replace(question_text, "([^(]*)\\(.*", "\\1"),
            # `Response Categories` = response_categories,
            `Dispersion` = as.character(sprintf("%.2f", dispersion)),
            `Difficulties` = difficulties,
            `Survey Dataset Codes*` = all_surveys) %>% 
  modelsummary::datasummary_df(output = "kableExtra",
                               longtable = TRUE,
                               title = "Survey Items Used to Estimate Public Gender Egalitarianism Scores",
                               escape = FALSE) %>% 
  kableExtra::kable_styling(latex_options = c("repeat_header"),
                            font_size = 7) %>%
  kableExtra::column_spec(1, width = "7em") %>%
  kableExtra::column_spec(2, width = "4em") %>%
  kableExtra::column_spec(3, width = "16em") %>%
  # kableExtra::column_spec(3, width = "13em") %>%
  kableExtra::column_spec(4, width = "4em") %>%
  kableExtra::column_spec(c(5, 6), width = "8em") %>%
  kableExtra::footnote(symbol = "Survey dataset codes correspond to those used in the DCPOtools R package (Solt, Hu, and Tai 2019).")
```

\pagebreak
## Appendix B: Source Data Observations by Country and Year
```{r obs1, fig.cap = "Source Data Observations by Country and Year", fig.height = 7}
#| label: fig-obs1

dcpo_input_plot <- dcpo_input_raw_pge1 %>% 
  filter(country %in% oecd_countries) %>% 
  distinct(country, year, item, cc_rank) %>% 
  group_by(country, year) %>% 
  summarize(n = n(),
            cc_rank = mean(cc_rank)) %>% 
  ungroup() 

dcpo_input_plot %>%
  ggplot(aes(x = year, 
             y = forcats::fct_reorder(country, cc_rank),
             fill = n)) + 
  geom_tile() +
  scale_fill_steps(low = rev(hcl.colors(8, "inferno"))[1],
                   high = rev(hcl.colors(8, "inferno"))[8],
                   breaks =  seq(2, 16, 2),
                   show.limits = TRUE,
                   right = FALSE,
                   name = "Observations") +
  labs(x = NULL, y = NULL) +
  scale_x_continuous(breaks=seq(1968, 2024, 4),
                     sec.axis = dup_axis()) +
  scale_y_discrete(position = "right") +
  theme(axis.text.x  = element_text(size = 6),
        axis.text.y  = element_text(size = 7),
        strip.background = element_rect(fill = "white", colour = "white"),
        strip.placement = "outside",
        legend.position = "bottom",
        # legend.position = c(0.13, 0.12),
        legend.background = element_rect(fill = "white", colour = NA))
```

